



THis is a version of test finally used for 6 & 10 lists tests


# library
```{r}
# library(Rmisc)
library(dplyr)
library(tidyverse)
library(readr)
'%notin%' <- function(x,y)!('%in%'(x,y));
```


```{r}
filepath=c("data-design2/visualexp-forward (1).csv")
df = readr::read_csv(filepath)
```


# Read files


```{r}
dfimp=
  df%>% 
  filter(is_finished==1,codeversion%in%c(1,2))%>%
  # group_by(condition,PROLIFIC_PID,all_accumulated_accuracy,recorded_at)%>%
  group_by(condition,PROLIFIC_PID,all_accumulated_accuracy,run_id)%>%
  summarize(n=n())%>%
  # group_by(condition)%>%
  # summarize(n=n())%>%
  # filter(PROLIFIC_PID%in%c("62732f7ea28589a21f63b1ee"))%>%
  # filter(all_accumulated_accuracy<0.6)%>%
  # filter(condition=="b")%>%
  mutate()
dfimp
```



## check and get txt file
```{r}
# now$`Participant id`
now = read_csv("data/temp2/export5.csv")%>%
  filter(Status=="AWAITING REVIEW")%>%
  mutate(id = `Participant id`)%>%
  mutate(acc = case_when(id%in%dfimp$PROLIFIC_PID ~1))%>%
  select(id,acc)%>%
  filter(acc==1)
  # filter(id ==)
write.table(now$id, file = "data/temp2/out.txt", sep = "\t",quote=FALSE,row.names = FALSE)

dfimp$all_accumulated_accuracy[dfimp$ip=="76.112.5.227"]
```



See who prioritize in answering the second word when first answers none

```{r}
df %>% filter(wordanswer_first=="none"& is_correct_second & wordanswer_second!="none")%>%
  select(wordanswer_first,wordanswer_second,wordcondi,ip)
```
```{r}
testdf <- data.frame(
  Name = c("Alice", "Bob", "Charlie", "David"),
  City = c("New York", "San Francisco", "Los Angeles", "Chicago"),
  # Occupation = c("Engineer", "Teacher", "Artist", "Doctor"),
  StringsColumn = c("Alice", "ss", "Charlie", "Chicago")
)
class(testdf$Name)
testdf %>% mutate( is_same = StringsColumn %in% c(Name,City))
```


## check
```{r}
# df%>%filter(is_finished==1,codeversion==3) %>%
#   filter(all_accumulated_accuracy>0.6)%>%
#   group_by(PROLIFIC_PID)%>%
#   summarize(n=n())%>%
#   filter(n>1410)
# 
# #done twice: 62b0ff84054c6ca32f481c65;63e5a6690eeedc20da056717
# df%>%filter(is_finished==1,codeversion==3) %>%
#   filter(all_accumulated_accuracy>0.6)%>%
#   group_by(condition,PROLIFIC_PID,recorded_at)%>%
#   filter(PROLIFIC_PID%in%c("62b0ff84054c6ca32f481c65","63e5a6690eeedc20da056717"))%>%
#   summarize(n=n())


# 62b0ff84054c6ca32f481c65: delete f condition
# 63e5a6690eeedc20da056717: delete r condition
dfchanged =
  df %>%
  filter(is_finished==1,codeversion%in%c(1,2)) %>%
  # mutate(is_correct_first_crt2=case_when(is_correct_first&wordanswer_first!="none"~1,
  #                                        TRUE ~ 0),
  #        is_correct_second_crt2=case_when(is_correct_second&wordanswer_second!="none"~1,
  #                                         TRUE~0),
  #        is_correct_final_oneinrepeat = is_correct_first_crt2+is_correct_second_crt2==1 & wordcondi=="repeat",#only 1 correct
  #        is_correct_final_twoinrepeat = is_bothcorrect & wordcondi=="repeat",#only 2 correct
  #        is_correct_final_oneinunique =  is_correct_first_crt2+is_correct_second_crt2==1 & wordcondi=="unique"
  #        )%>%
  #should the following onecorrect in final test be at least one correct?!!!!!!!!
  # mutate(OneCorrectInFinalTest=case_when(task%in%c("pretest_response","counting_response")~correct,
  #                                        task=="finalt_response"~is_correct_final_oneinrepeat|is_correct_final_oneinunique),
  #        AllCorrectInFinalTest=case_when(task%in%c("pretest_response","counting_response")~correct,
  #                                        task=="finalt_response"~is_correct_final_twoinrepeat|is_correct_final_oneinunique))%>%
  # mutate(task_numcorrect=case_when(task=="finalt_response"&OneCorrectInFinalTest~"FinalTest-OneCorrect",
  #                                  task=="finalt_response"&AllCorrectInFinalTest~"FinalTest-BothCorrect",
  #                                  task=="pretest_response"~"InitialTest",
  #                                  task=="counting_response"~"counting",
  #                                  TRUE~task))%>%
  # mutate(correct = case_when(
  #   task=="finalt_response" & wordcondi=="unique"~is_correct_final_oneinunique,
  #   task=="finalt_response" & wordcondi=="repeat"~is_correct_first_crt2+is_correct_second_crt2,
  #   TRUE~correct))%>%
  mutate(listnumber_1to10=as.factor(listnumber_1to10))%>%
  mutate(condition=case_when(condition=="b"~"backward",condition=="f"~"forward",condition=="r"~"random"))%>%
  mutate(wordleft_correct_repeat=case_when(wordcondi=="repeat" & (word_left_i==wordanswer_first|word_left_i==wordanswer_second) ~ 1,
                                    wordcondi=="repeat" & !(word_left_i==wordanswer_first|word_left_i==wordanswer_second) ~ 0,
                                    TRUE ~ NA),
         
         wordright_correct_repeat=case_when(wordcondi=="repeat" & (word_right_i==wordanswer_first|word_right_i==wordanswer_second) ~ 1,
                                     wordcondi=="repeat" & !(word_right_i==wordanswer_first|word_right_i==wordanswer_second) ~ 0,
                                    TRUE ~ NA))%>%
  pivot_longer(cols=c(wordleft_correct_repeat,wordright_correct_repeat),
               names_to = "word_leftorright",
               values_to = "correct_finaltest_repeat")%>%
  mutate(word_leftorright = case_when(word_leftorright=="wordleft_correct_repeat"~"word_left",
                                      word_leftorright=="wordright_correct_repeat"~"word_right"))%>%
  filter(!(word_leftorright == "word_right" & !(wordcondi == "repeat" & task == "finalt_response")))%>%
  mutate(word_leftorright=case_when(is.na(correct_finaltest_repeat)~"none",
                                    TRUE~word_leftorright))%>%
  mutate(correct = case_when(task=="finalt_response"& wordcondi=="repeat"~correct_finaltest_repeat,
                             task=="finalt_response"& wordcondi=="unique"~ (word_left_i==wordanswer_first|word_left_i==wordanswer_second),
                             TRUE~correct))%>%
  filter(ip%notin%c("76.112.5.227"))%>%
  mutate()


dfchanged %>% 
  filter(task%in%c("finalt_response")) %>%
  # mutate(is_correct_final_oneinunique=as.numeric(is_correct_final_oneinunique))%>%
  select(condition,ip,is_test_inpair1,is_test_inpair2,wordcondi,word_leftorright,correct_finaltest_repeat,correct,
         word_response,wordchosen_finaltest)
# dfchanged$correct_finaltest


dfchanged%>% #check number of participant in each condition
  filter(is_finished==1,codeversion%in%c(1,2))%>%
  group_by(condition,PROLIFIC_PID)%>%
  summarize(n=n())%>%
  group_by(condition)%>%
  summarize(n=n())

dfchanged %>%
  # filter(task=="finalt_response"&ct<0.25,trial==5)%>%
  # filter(ip=="76.112.5.227")%>%
  filter(listnumber_1to10==1,task=="finalt_response")%>%
  select(ip,is_correct_first,wordcondi,is_correct_second,wordanswer_first,wordanswer_second,OneCorrectInFinalTest)%>%
  mutate()

dfchanged %>%
  # filter(ip=="76.112.5.227")%>%
  group_by(condition,ip,PROLIFIC_PID,all_accumulated_accuracy)%>%
  summarize(mean(all_accumulated_accuracy))%>%
  mutate()
  
```

```{r}
dfchanged %>% 
  filter(task%in%c("finalt_response")) %>%
  mutate(is_correct_final_oneinunique=as.numeric(is_correct_final_oneinunique))%>%
  select(condition,ip,wordcondi,task,word_leftorright,correct_finaltest_repeat,is_correct_final_oneinunique,is_correct_first_crt2,is_correct_second_crt2,correct,
         word_response,wordchosen_finaltest,is_uniquecorrect,wordanswer_first,wordanswer_second,word_left_i)
```


## calculate mean
```{r}
dfnew=
  dfchanged %>% 
  filter(task%in%c("pretest_response","finalt_response","counting_response")) %>%
  # filter(task%in%c("pretest_response","finalt_response")) %>% 
  mutate(trial = case_when(task=="counting_response"~as.factor(trialnum),
                           TRUE~listnumber_1to10) ) %>%
  group_by(condition,ip,trial,wordcondi,task) %>%
  summarise(ct = mean(correct)) %>%
  group_by(condition,ip,task,wordcondi) %>% #average across lists (trial)
  mutate(ct = case_when(task=="counting_response"~mean(ct),
                           TRUE~ct))%>%
  ungroup()



dfnew
dfnew%>%
         # filter(ip %notin% c("68.80.89.47"))%>%
         group_by(condition,task,trial,wordcondi)%>%
         summarize(ct=mean(ct))
```

Previous:


ggplot(data=dfnew%>%
         mutate(wordcondi=case_when(task=="counting_response"~"counting task, no wordcondition",
                                    TRUE~wordcondi))%>%
         filter(AccuracyCriteria=="AllCorrectInFinalTest")%>%
         group_by(condition,ip,task,trial)%>%
         summarize(ct=mean(ct))%>%
         mutate()
       )+
  geom_point(aes(trial,ct,group=ip))+
  geom_line(aes(trial,ct,group=interaction(task,ip),color=ip))+
  facet_grid(task~condition)+
  labs(title="Data by task and condition for each participant")+
  theme(legend.position = "bottom")+theme(text = element_text(size = 20))
  
### throw out people
```{r}
# 47.158.129.211 excluded for low pretest, 68.225.203.42  low counting and final test 
ggplot(data=dfnew%>%
         mutate(wordcondi=case_when(task=="counting_response"~"counting task, no wordcondition",
                                    TRUE~wordcondi))%>%
         filter(ip!="76.112.5.227")%>%
         # filter(AccuracyCriteria=="OneCorrectInFinalTest")%>%
         group_by(condition,ip,task,trial)%>%
         summarize(ct=mean(ct))%>%
         mutate()
       )+
  geom_point(aes(trial,ct,group=ip))+
  geom_line(aes(trial,ct,group=interaction(task,ip),color=ip))+
  facet_grid(task~condition)+
  labs(title="Data by task and condition for each participant")+
  theme(legend.position = "bottom")+theme(text = element_text(size = 20))

# df %>% filter(ip=="174.45.226.170")%>%group_by(condition,PROLIFIC_PID)%>%summarize(n=1)

ggplot(data=dfnew%>%
         # filter(ip %notin% c("68.80.89.47"))%>%
         group_by(condition,task,trial,wordcondi)%>%
         summarize(ct=mean(ct))%>%
         mutate(wordcondi=case_when(task=="counting_response"~"counting task, no wordcondition",
                                    TRUE~wordcondi))
       )+
  geom_point(aes(trial,ct))+
  geom_line(aes(trial,ct,group=interaction(wordcondi,task),color=task,linetype=wordcondi),size=1)+
  facet_grid(.~condition)+
  labs(x="list number",y="accuracy")+theme(text = element_text(size = 20))
```


#  plot by is tested in intial 

```{r}

dfnew1=
  dfchanged %>% 
  # mutate(is_tested = (task=="finalt_response"& (is_test_inpair1=="1"|is_test_inpair2=="1"))|
  #          task=="pretest_response"|(task=="finalt_response" & wordcondi=="unique") )%>%
    mutate(is_tested = case_when(
      task=="finalt_response"& word_leftorright=="word_left" ~ is_test_inpair1=="1",
      task=="finalt_response"& word_leftorright=="word_right" ~ is_test_inpair2=="1",
      task=="pretest_response" ~ is_test,
      task=="counting_response"~1,
      TRUE~ is_test
      ))%>%
  # pivot_longer(cols=c(is_test_inpair1,is_test_inpair2),names_to="")%>%
  filter(task%in%c("pretest_response","finalt_response","counting_response")) %>%
  # filter(task%in%c("pretest_response","finalt_response")) %>% 
  mutate(trial = case_when(task=="counting_response"~as.factor(trialnum),
                           TRUE~listnumber_1to10) ) %>%
  group_by(condition,ip,trial,wordcondi,task,is_tested) %>%
  summarise(ct = mean(correct)) %>%
  group_by(condition,ip,task,wordcondi,is_tested) %>% #average across lists (trial)
  mutate(ct = case_when(task=="counting_response"~mean(ct),
                           TRUE~ct))%>%
  ungroup()
dfnew1$is_tested%>%summary()
ggplot(data=dfnew1%>%
         # filter(ip %notin% c("68.80.89.47"))%>%
         group_by(condition,task,trial,wordcondi,is_tested)%>%
         summarize(ct=mean(ct))%>%
         mutate(wordcondi=case_when(task=="counting_response"~"counting task, no wordcondition",
                                    TRUE~wordcondi))%>%
         mutate(is_tested=as.factor(is_tested))
       )+
  geom_point(aes(trial,ct))+
  geom_line(aes(trial,ct,group=interaction(wordcondi,is_tested),color=interaction(wordcondi),linetype=is_tested),size=1)+
  facet_grid(task~condition)+
  labs(x="list number",y="accuracy",color="word condition ",linetype="is tested in intial")+
  theme(text = element_text(size = 20))
  # scale_linetype_manual(values=c(4,1,2,3))
```





# plot by if it's first or second pair (left or right)
```{r}
dfnew3=
  dfchanged %>% 
  # mutate(is_tested = is_test_inpair1=="1"|is_test_inpair2=="1")%>%
  # pivot_longer(cols=c(is_test_inpair1,is_test_inpair2),names_to="")%>%
  filter(task%in%c("pretest_response","finalt_response","counting_response")) %>%
  # filter(task%in%c("pretest_response","finalt_response")) %>% 
  mutate(trial = case_when(task=="counting_response"~as.factor(trialnum),
                           TRUE~listnumber_1to10) ) %>%
  group_by(condition,ip,trial,wordcondi,task,word_leftorright) %>%
  summarise(ct = mean(correct)) %>%
  group_by(condition,ip,task,wordcondi,word_leftorright) %>% #average across lists (trial)
  mutate(ct = case_when(task=="counting_response"~mean(ct),
                           TRUE~ct))%>%
  ungroup()%>%
         # filter(ip %notin% c("68.80.89.47"))%>%
         group_by(condition,task,trial,wordcondi,word_leftorright)%>%
         summarize(ct=mean(ct))%>%
         mutate(wordcondi=case_when(task=="counting_response"~"counting task, no wordcondition",
                                    TRUE~wordcondi))
dfnew3%>%filter(task=="pretest_response",trial==1,condition=="backward")

ggplot(data=dfnew3%>%filter(task=="finalt_response")%>%
         mutate(word_leftorright=case_when(word_leftorright=="word_left"~"word studied in pair1",
                                           word_leftorright=="word_right"~"word studied in pair2",
                                           TRUE~word_leftorright))
       )+
  geom_point(aes(trial,ct))+
  # geom_line(aes(trial,ct,group=interaction(wordcondi,word_leftorright),linetype=wordcondi),size=1)+
  facet_grid(task~condition)+
  geom_line(aes(trial,ct,group=interaction(wordcondi,word_leftorright),color=interaction(wordcondi,word_leftorright)),size=1)+
  labs(x="list number",y="accuracy",color="Word Condition and if it's word from pair1or2")+
  theme_minimal()+
  theme(text = element_text(size = 20),legend.position = "bottom")+
  theme()+
   guides(
    color = guide_legend(
      title.position = "top",
      nrow = 2  # Adjust the number of rows as needed
    )
  )
  # scale_linetype_manual(values=c(3,1,2))
```


```{r}
dfnew4=
  dfchanged %>% 
  # mutate(is_tested = is_test_inpair1=="1"|is_test_inpair2=="1")%>%
  # pivot_longer(cols=c(is_test_inpair1,is_test_inpair2),names_to="")%>%
  filter(task%in%c("pretest_response","finalt_response","counting_response")) %>%
  # filter(task%in%c("pretest_response","finalt_response")) %>% 
  mutate(trial = case_when(task=="counting_response"~as.factor(trialnum),
                           TRUE~listnumber_1to10) ) %>%
  group_by(condition,ip,trial,wordcondi,task,pairs_which_1or2) %>%
  summarise(ct = mean(correct)) %>%
  group_by(condition,ip,task,wordcondi,pairs_which_1or2) %>% #average across lists (trial)
  mutate(ct = case_when(task=="counting_response"~mean(ct),
                           TRUE~ct))%>%
  ungroup()%>%
         # filter(ip %notin% c("68.80.89.47"))%>%
         group_by(condition,task,trial,wordcondi,pairs_which_1or2)%>%
         summarize(ct=mean(ct))%>%
         mutate(wordcondi=case_when(task=="counting_response"~"counting task, no wordcondition",
                                    TRUE~wordcondi))
dfnew3%>%filter(task=="pretest_response",trial==1,condition=="backward")

ggplot(data=dfnew4%>%filter(task=="pretest_response")%>%
         mutate(pairs_which_1or2=case_when(wordcondi=="unique"~0,
                                           TRUE~pairs_which_1or2))
       )+
  geom_point(aes(trial,ct))+
  # geom_line(aes(trial,ct,group=interaction(wordcondi,word_leftorright),linetype=wordcondi),size=1)+
  facet_grid(task~condition)+
  geom_line(aes(trial,ct,group=interaction(wordcondi,pairs_which_1or2),color=interaction(wordcondi,pairs_which_1or2)),size=1)+
  labs(x="list number",y="accuracy",color="Word Condition and if it's word from pair1or2")+
  theme_minimal()+
  theme(text = element_text(size = 20),legend.position = "bottom")+
  theme()+
   guides(
    color = guide_legend(
      title.position = "top",
      nrow = 2  # Adjust the number of rows as needed
    )
  )
```



# conditional plot
  # mutate(
  #     conditional_correct = case_when(
  #       task == "finalt_response" ~ 
  #         sapply(word_chosen, function(word) {
  #           match_row <- which(word %in% df$word_chosen & df$task == "pretest_response")
  #           if (length(match_row) > 0) {
  #             df$correct[match_row[1]]
  #           } else {
  #             NA
  #           }
  #         }),
  #       TRUE ~ NA_real_
  #     )
  #   )

```{r}
a1=dfchanged %>% 
  mutate(word_chosen = case_when(task=="pretest_response"~wordchosen_initial,
                                 task=="finalt_response" & wordcondi=="repeat"&word_leftorright=="word_left"~wordchosen_inpair1,
                                 task=="finalt_response" & wordcondi=="repeat"&word_leftorright=="word_right"~wordchosen_inpair2,
                                 task=="finalt_response" & wordcondi=="unique" ~ wordchosen_initial
                                 ))%>%
  select(condition,ip,trial_index,listnumber_1to10,wordcondi,task,word_chosen,correct)%>%filter(task%in%c("pretest_response","finalt_response"))
a1
a2=a1%>%
  left_join(
      a1 %>% filter(task == "pretest_response") %>% select(word_chosen, correct,ip,condition,listnumber_1to10),
      by = c("word_chosen","ip","condition","listnumber_1to10"),
      suffix = c("", "_pretest")
    ) %>%
  mutate(
    conditional_correct = case_when(
      task == "finalt_response" ~ correct_pretest,
      TRUE ~ NA_real_
    )
  ) %>% filter(!is.na(conditional_correct))
a2
  # mutate()
  # select(-correct_pretest)
# %>%
  # select(condition,ip,wordcondi,task,conditional_correct,word_chosen,correct_pretest,conditional_correct)%>%
  # filter(task%in%c("pretest_response","finalt_response"))
```


```{r}
dfnew4=
  a2%>%
  filter(task%in%c("finalt_response")) %>%
  mutate(trial = listnumber_1to10 ) %>%
  group_by(condition,ip,trial,wordcondi,task,conditional_correct) %>%
  summarise(ct = mean(correct)) %>%
  ungroup()%>%
  group_by(condition,task,trial,wordcondi,conditional_correct)%>%
  summarize(ct=mean(ct))
dfnew4



ggplot(data=dfnew4%>%filter(task=="finalt_response")       )+
  geom_point(aes(trial,ct))+
  # geom_line(aes(trial,ct,group=interaction(wordcondi,word_leftorright),linetype=wordcondi),size=1)+
  facet_grid(task~condition)+
  geom_line(aes(trial,ct,group=interaction(wordcondi,conditional_correct),color=interaction(wordcondi,conditional_correct)),size=1)+
  labs(x="list number",y="accuracy",color="Word Condition and if correct in intial test ")+
  theme_minimal()+
  theme(text = element_text(size = 20),legend.position = "bottom")+
  theme()+
   guides(
    color = guide_legend(
      title.position = "top",
      nrow = 2  # Adjust the number of rows as needed
    )
  )
```



























