
 # File now
   # Example of a valid .lintr file
    
linters: with_defaults(
  line_length_linter = line_length_linter(80),
  object_name_linter = NULL
)   

```{r}
# .libPaths()
library(grDevices)
options(bitmapType='cairo')
```

## library

```{r} 
# options(lintr.linter_file = NULL) # Disable .lintr file
# lintr::lint("your_file.R", linters = with_defaults(line_length_linter = NULL)) # Disable line length linter
# output: html_document
library(here)
here::i_am("design3/data_analysis/R_design3_pilotExample.rmd")
print(here())
library(ggplot2) 
library(forcats) # for fct_relevel
# library()
library(dplyr)
# library(gridExtrau
library(tidyr)  
# library(rstudioapi)

```


# Read Data

```{r}
# filepath=c("data-design3/ekstra_debugv1.csv")
# setwd(dirname(rstudioapi::getSourceEditorContext()$path))
getwd()
# df_pl = read.csv("data-design3/IMUSE-V1toV2,n30.csv")%>%mutate(correct=case_when(correct=="true"~1,correct=="false"~0,TRUE~ NA))%>%
df_pl1 = read.csv(here("design3","data", "IMUSE-V1.3andHigher,n48.csv"))%>%mutate(correct=case_when(correct=="true"~1,correct=="false"~0,TRUE~ NA))%>%
  mutate(listNum_appear0_initial = as.numeric(listNum_appear0_initial))%>%mutate(codeversion=1.3)
# df_pl2$codeversion
df_pl2 = read.csv(here("design3","data", "IMUSE-V1toV2,n30.csv"))%>%mutate(correct=case_when(correct=="true"~1,correct=="false"~0,TRUE~ NA))%>%
  mutate(listNum_appear0_initial = as.numeric(listNum_appear0_initial))

df_pl3 = read.csv(here("design3","data", "IMUSE-v1.4n20.csv"))%>%mutate(correct=case_when(correct=="true"~1,correct=="false"~0,TRUE~ NA))%>%
  mutate(listNum_appear0_initial = as.numeric(listNum_appear0_initial))

df_pltest2 = read.csv(here("design3","data", "IMUSE-V5_second 12.csv"))%>%mutate(correct=case_when(correct=="true"~1,correct=="false"~0,TRUE~ NA))%>%
  mutate(listNum_appear0_initial = as.numeric(listNum_appear0_initial))

df_pltest3 = read.csv(here("design3","data", "IMUSE-V5_first35.csv"))%>%mutate(correct=case_when(correct=="true"~1,correct=="false"~0,TRUE~ NA))%>%
  mutate(listNum_appear0_initial = as.numeric(listNum_appear0_initial))
df_pltest4 = read.csv(here("design3","data", "IMUSE-V5_third .csv"))%>%mutate(correct=case_when(correct=="true"~1,correct=="false"~0,TRUE~ NA))%>%
  mutate(listNum_appear0_initial = as.numeric(listNum_appear0_initial))
df_pltest=rbind(df_pltest2,df_pltest3 )
df_pl=rbind(df_pl1,df_pl2,df_pl3,df_pltest2,df_pltest3,df_pltest4)
# df_pl=rbind(df_pltest2,df_pltest3,df_pltest4)
# df_pl=rbind(df_pl1,df_pl2)
# df_pl1
# df_pl2
names(df_pl)
df_pl

#67d9bb21800df9410d2d2a16; 566a19b57da035000fb39b89
df_pl%>%filter(is_finished==1)%>%
  group_by(subject_id)%>%
  summarize(nn=n())
  # filter(nn>1265)

df_pltest %>% filter(is_finished==1, PROLIFIC_PID!="")%>%
  group_by(PROLIFIC_PID)%>%
  summarize(n=n(),ac=mean(all_accumulated_accuracy))

df_pltest3 %>% filter(is_finished==1, PROLIFIC_PID!="")%>%
  group_by(PROLIFIC_PID)%>%
  summarize(n=n(),ac=mean(all_accumulated_accuracy))

#detect the duplicated lins in df_pl and delete them (can use dplyr or tyidr etc)
# Create a function that takes two numbers and returns their sum


# df %>% filter
# df_pl%>%filter(subject_id=="566a19b57da035000fb39b89")%>%
#   filter(task=="surveyatend")
# 
# df_pl %>% unique()%>%filter(subject_id=="566a19b57da035000fb39b89")%>%
#   filter(task=="surveyatend")
# df_pl%>%filter(subject_id=="566a19b57da035000fb39b89")%>%
#   filter(task=="surveyatend")

 
df_pl%>%
  filter(is_finished==1)%>%
  filter(subject_id!="")%>%
  group_by(subject_id) %>%
  summarise(n = n())

```




 individual diff

initial test

6100434d983910e711b3a504 #this subject had bluetooth keyboard not working well in fiinal test
:: "I experienced a technical issue with my own keyboard (as it's bluetooth) it died and wasn't registering my answers for a portion of the last section.
67d220de3ad5d3f4be7836bd	#didn't finish all, returned its data
67f909f80373c9f5af736a5a #got veryvery low allaccuracy - 20% and chekcing the data, it is especially bad at final test, but good in intial test
67ecdf3dcb59c5e0f274ad2d #did the experiment twice:
    recorded_at
    <chr>
    nm
    <int>
    2025-04-14 08:09:41	5			
    2025-04-14 08:47:36	324			
    2025-04-14 09:12:40	1263	


## Add firestone data
lost:
67e4ae4138a215b586f1355c
6767e3338fb21303557a8903
67eade9122bddfb4cd165d09


```{r}
# library(jsonlite)
file_name <- "test1.overall_export_metadata"
full_file_path <- "/home/lea/Insync/naszhu@gmail.com/Google Drive/shulai@iu.edu 2022-09-04 14:28/IUB/Prj_tmp/data/participants_finished_final_trials_finished.csv"

dreal = read.csv(full_file_path) #%>%filter(subject_id%in%c("67dc712c511053c8d90e2c29","67eac4d6bf3d1c4df7bd65df","67ed4e79983b8a8ba5517548") )
common_cols <- intersect(names(df_pl), names(dreal))

print(paste("Common columns:", paste(common_cols, collapse=", ")))

target_classes <- lapply(df_pl[common_cols], function(col) class(col)[1])


f2_aligned <- dreal %>%
  mutate(across(all_of(common_cols), ~ {

    col_name <- cur_column()
    target_class <- target_classes[[col_name]]
    current_col_data <- .x
    switch(target_class,
           "character" = as.character(current_col_data),
           "numeric"   = as.numeric(current_col_data),
           "integer"   = as.integer(current_col_data),
           "logical"   = as.logical(current_col_data),
           "factor"    = factor(current_col_data), #
           current_col_data
           )
  }))
f2_aligned%>%group_by(subject_id)%>%
  summarize(n=n())

# df_pl_combine = bind_rows(df_pl, dreal)


# df_pl_combine%>%filter(subject_id=="thisis_cool")%>%arrange(trial_index) 
# df_pl_combine%>%group_by(subject_id)%>%
#   summarize(n=n(),
#     ac=mean(all_accumulated_accuracy),
#             isf=mean(is_finished))
# 
# df_pl_combine%>%filter(subject_id%in%c("67dc712c511053c8d90e2c29","67eac4d6bf3d1c4df7bd65df","67ed4e79983b8a8ba5517548"))
# 
# dreal%>%group_by(subject_id)%>%
#   summarize(n=n())
```


## dreal-finaldatasave- a full new way of binding
```{r}

file_name <- "test1.overall_export_metadata"
full_file_path <- "/home/lea/Insync/naszhu@gmail.com/Google Drive/shulai@iu.edu 2022-09-04 14:28/IUB/Prj_tmp/data/participants_finished_final_trials_finished.csv"
full_file_path_er <- "/home/lea/Insync/naszhu@gmail.com/Google Drive/shulai@iu.edu 2022-09-04 14:28/IUB/Prj_tmp/data/participants_trials_backup_ealier.csv"
full_file_path_backup <- "/home/lea/Insync/naszhu@gmail.com/Google Drive/shulai@iu.edu 2022-09-04 14:28/IUB/Prj_tmp/data/participants_trials_backup_backup.csv"

# dreal_earlier = read.csv(full_file_path_er)%>% 
# the following are the 4 people who finished  the experiment in data file dreal_er, and they used the firebase version of only backup trials (i.e., not finished triales), they did not have the all_accumulated_accuracy attached as whole column, so need to assign manually
##############3 participants_trials_backup_ealier.csv
passlist = c("673ccb0691efe91cd015dcf7","67dc712c511053c8d90e2c29","67eac4d6bf3d1c4df7bd65df","67ed4e79983b8a8ba5517548") 
acc_accuray=c(0.5631313,0.5643939,0.6742424,0.8674242)
dreal_er = read.csv(full_file_path_er)%>% 
  mutate(is_finished=case_when(subject_id%in%passlist ~ 1,
                               TRUE ~ is_finished))%>%
  mutate(all_accumulated_accuracy=case_when(subject_id=="673ccb0691efe91cd015dcf7" ~ acc_accuray[1],
                                            subject_id=="67dc712c511053c8d90e2c29" ~ acc_accuray[2],
                                            subject_id=="67eac4d6bf3d1c4df7bd65df" ~ acc_accuray[3],
                                            subject_id=="67ed4e79983b8a8ba5517548" ~ acc_accuray[4],
                                            TRUE ~ all_accumulated_accuracy))%>%
  filter(is_finished==1)

dreal_er%>%group_by(subject_id)%>%
  summarize(n=n(),isf=mean(is_finished),acc=mean(all_accumulated_accuracy))
# dreal_er%>%filter(!is.na(all_accumulated_accuracy))%>%select(subject_id,all_accumulated_accuracy)

################# participants_trials_backup_backup.csv
# passlist2=c("5f9389fafdbecb173b329cca", "5fb39a485655aa025926ad30", "6307f3c967020d1202332b77", 
#   "63268ad93b6ecc1acf782a21", "63c1d184883ce15537788b40", "65c118f1cd19001157ace3a0", 
#   "66cfb3d040139a5cfd914312", "66e8661e0c5e57cda7bf2d39", "673a27fe372ce97a95aecf5c", 
#   "6741ce8667002c96f0362d34", "6751acc5dc78128951a34f1f", "67558204d75dd7351fe9d17e", 
#   "678c0d73fea9aaf55cd880be", "67c1a72590fcbf99458bb1f2", "67dc0e92b55a4d630f52e765", 
#   "67e069199f5b036960b0cc5f", "67e2fdf2d328f1e3dd7045b6", "67e8446d006a6c155f71bd2d", 
#   "67e9875c5b9b26c19a3bdf88", "67eaf90db55644f3c56fffa9", "67eb2ab3bd8cba1852857e2d", 
#   "67edb211a7c1d23c1535d6b2", "67eefac7eaf3702ddd603092", "67f05ce092cdcc0392692398", 
#   "67fff6438bb63725ca004b27")

mm=read.csv(full_file_path_backup)%>%filter(is_finished==1)%>%
  group_by(subject_id)%>%
  summarize(n=n(),isf=mean(is_finished),acc=mean(all_accumulated_accuracy))
passlist2=mm$subject_id
mm_allacc=read.csv(full_file_path_backup)%>%filter(!is.na(all_accumulated_accuracy))%>%
  select(subject_id,all_accumulated_accuracy)

dreal_backup = read.csv(full_file_path_backup)%>% #%>%filter(is_finished==1)%>%
  mutate(is_finished=case_when(subject_id%in%passlist2 ~ 1,
                               TRUE ~ is_finished))%>%
  filter(is_finished==1)%>%arrange(subject_id)%>%
  select(-all_accumulated_accuracy)%>%
  left_join(mm_allacc,by="subject_id")

dreal_backup%>%group_by(subject_id)%>%
  summarize(n=n(),isf=mean(is_finished),acc=mean(all_accumulated_accuracy))

dreal_backup 
dreal0 = read.csv(full_file_path)


dreal = full_join(dreal0,dreal_er)


# keep a copy of the original
dreal_orig <- dreal

# align classes, but only map "true"/"false" strings when target is logical
f2_aligned <- dreal %>%
  mutate(across(all_of(common_cols), ~{
    col <- cur_column()
    tgt <- target_classes[[col]]
    x   <- .

    # if original is character, detect "true"/"false"
    if (is.character(x)) {
      xl <- tolower(x)
      bool_idx <- xl %in% c("true","false","t","f")
      if (any(bool_idx)) {
        if (tgt %in% c("numeric","integer")) {
          # map to "1"/"0" for numeric/integer
          x[bool_idx] <- ifelse(xl[bool_idx] %in% c("true","t"), "1", "0")
        } else if (tgt == "logical") {
          # map to logical TRUE/FALSE
          x[bool_idx] <- xl[bool_idx]
        } else if (tgt == "character") {
          # just lowercase for character
          x[bool_idx] <- xl[bool_idx]
        }
      }
    }

    # convert to target class
    switch(tgt,
      character = as.character(x),
      numeric   = as.numeric(x),
      integer   = as.integer(x),
      logical   = as.logical(x),
      factor    = factor(x),
      x
    )
  }))

# 2) which cols changed class?
orig_cls <- sapply(dreal_orig[common_cols], class)
new_cls  <- sapply(f2_aligned[common_cols], class)
changed  <- common_cols[orig_cls != new_cls]
cat("Columns with changed classes:\n")
print(data.frame(column = changed, before = orig_cls[changed], after = new_cls[changed]))

# 3) sample before/after values
for (col in changed) {
  cat("\n---", col, "---\n")
  print(tibble(
    row    = 1:5,
    before = dreal_orig[[col]][1:5],
    after  = f2_aligned[[col]][1:5]
  ))
}

# 4) print levels of all factor‐able cols in df_pl, dreal_orig, and f2_aligned
factor_cols <- intersect(common_cols, names(target_classes)[target_classes == "factor"])
for (col in factor_cols) {
  cat("\n=== Levels for column:", col, "===\n")
  cat("df_pl:\n");      print(levels(as.factor(df_pl[[col]])))
  cat("dreal_orig:\n"); print(levels(as.factor(dreal_orig[[col]])))
  cat("f2_aligned:\n"); print(levels(as.factor(f2_aligned[[col]])))
}

# 5) summary as before
f2_aligned %>%
  group_by(subject_id) %>%
  summarise(n = n())


combined_df = full_join(df_pl,f2_aligned)

f2_aligned %>% 
  filter(is_finished==1)%>%
  group_by(subject_id)%>%
  summarize(n=n(), all_accumulated_accuracy= mean(all_accumulated_accuracy))

read.csv(full_file_path)%>%filter(subject_id=="680ebf035ab59d342f31726e")
 
# [1] "680ebf035ab59d342f31726e" "67dc712c511053c8d90e2c29"
# [3] "67ed4e79983b8a8ba5517548" "67eac4d6bf3d1c4df7bd65df"
# dreal = full_join(dreal0,dreal_er)%>%full_join(dreal_backup)
# dreal_er%>%
combined_df%>%
  select(subject_id,is_finished)%>%
  filter(subject_id=="67eac4d6bf3d1c4df7bd65df")

combined_df%>%
  filter(is_finished==1)%>%
  group_by(subject_id)%>%
  summarize(n=n())
  # filter(subject_id=="67dc0e92b55a4d630f52e765")


```



# A tibble: 5 × 2
  subject_id                   n
  <chr>                    <int>
1 67d220de3ad5d3f4be7836bd   210
2 67db99eb2c3fa60d9e043a59   210
3 67dc0e92b55a4d630f52e765   240
4 67dea0a9723c135ffffe14f0   570
5 67eec102d37d56b29145e034    30

## print all levels
```{r}
levels(as.factor(f2_aligned$current_assignmentTypesWithinList )) ==
levels(as.factor(df_pl$current_assignmentTypesWithinList ))

levels(as.factor(f2_aligned$is_currentObjAppear1 ))==
levels(as.factor(df_pl$is_currentObjAppear1 ))


levels(as.factor(f2_aligned$type_comment ))==
levels(as.factor(df_pl$type_comment ))



```

```{r}
# df_rt_pl%>%
#   filter(codeversion!=1)%>%
#   group_by(subject_id)%>%
#   summarize(n=n())
```

codeversion1: [1] "67eecbd7a0c98bad9a91d0c0" "67ef6e8e9bfc15c060497365"
runid 5 (id: 67eecbd7a0c98bad9a91d0c0) source code version: 7dfe7f81cd9c80a1972070b6eed80b27 		2025-04-04 12:03:51
runid 4: 800ada036aababc29b2738b065f35859 2025-04-19 04:58:17
runid 6: 800ada036aababc29b2738b065f35859 2025-04-19 04:58:31

id (67ef6e8e9bfc15c060497365)
codev: 7dfe7f81cd9c80a1972070b6eed80b27
runat: 2025-04-04 12:10:35
runid: 6

```{r}
ds=
combined_df%>% filter(task%in% c("initialTest_response","finalTest")) %>% 
  filter(is_finished==1)%>%
  filter(run_id==4)%>%
  # filter(subject_id=="67ef6e8e9bfc15c060497365")%>%
  # mutate()
  # filter(stimulusConditions=="B", testPos_appear1_initial==0)%>%
  select(codeversion,run_id)

levels(as.factor(ds$subject_id))

ds=combined_df%>%filter(codeversion==1,is_finished==1)
levels(as.factor(ds$subject_id))
# ds
```


## data clean
```{r}
levels(as.factor(df_pl$task ))

df_rt_pl =
  combined_df %>% filter(task%in% c("initialTest_response","finalTest")) %>% 
  filter(is_finished==1)%>%
  mutate(rt=as.numeric(rt))%>%
  filter(codeversion != 1)%>%
  filter(subject_id!="67ecdf3dcb59c5e0f274ad2d")%>%
  filter(! subject_id%in%c("6751acc5dc78128951a34f1f","67f909f80373c9f5af736a5a"))%>% #accuracy too low
    filter(subject_id!="")%>%
  filter(!is.na(rt),rt<3000)%>%
  # filter(id!=)%>%
    # select(id_picName,codeversion,task,subject_id,  rt, condition, stimulusConditions, stimulusConditionName_nPlusOneTrial, listNum_appear0_initial,correct,type_comment,listNum_infinalOrder,listNum_appear1_initial,listNum_appear2_initial, anRepeatedItem, testPos_final,testPos_appear0_initial,testPos_appear1_initial,testPos_appear2_initial,studyPos_appear0_initial,studyPos_appear1_initial,studyPos_appear2_initial ,is_finished,all_accumulated_accuracy, type_code_studiedCurr,type_code_testiedCurr,type_code_testiedNext,is_currentObjAppear1,current_assignmentTypesWithinList,listNum_infinalOrder, stimulusConditions, correct_appear2,correct_appear1)%>%
    mutate(type_comment_fn=case_when(
                                stimulusConditions=="B"~
                                  "Target: : started and tested at (n) ; Appear once",
                                stimulusConditions == "Cn"~
                                  "Studied-only (n); Foil (n+1)",
                                stimulusConditions =="Dn" ~ 
                                  "Target: studied and tested at (n), Foil (n+1)",
                                stimulusConditions=="A"~
                                  "Studied-only (n); Appear once",
                                stimulusConditions=="Fnn"~
                                  "Foil(n), Foil (n+1)",
                                stimulusConditions=="Fn"~
                                  "Foil(n); Appear once",
                                stimulusConditions=="FF" ~
                                  "Final Foil"))%>%
      mutate(typecomment_in = case_when(current_assignmentTypesWithinList =="T_target" & is_currentObjAppear1=="true" ~"Target",
                                is_currentObjAppear1=="false" & type_comment=="current target, in next trial, from last trial"  ~ "Inherented Foil - Last Target",
                                                                is_currentObjAppear1=="false" & type_comment=="studied only, in next trial, from last trial"  ~ "Inherented Foil - Last Studied Only",
                                                                is_currentObjAppear1=="false" & type_comment=="tested only, in next trial, from last trial"  ~ "Inherented Foil - Last Foil",
                                
                                  current_assignmentTypesWithinList =="T_foil"  ~"New Foil"))
  # mutate(type_comment=case_when(type_comment=="current target, in next trial" ~ "Target: studied and tested at (n), Foil (n+1)",
  #                               type_comment=="current target, not in next trial"~
  #                                 "Target: : started and tested at (n) ; Appear once",
  #                               type_comment == "studied only, in next trial"~
  #                                 "Studied-only (n); Foil (n+1)",
  #                               type_comment=="studied only, not in trial"~
  #                                 "Studied-only (n); Appear once",
  #                               type_comment=="tested only, in next trial"~
  #                                 "Foil(n), Foil (n+1)",
  #                               type_comment=="tested only, not in next trial"~
  #                                 "Foil(n); Appear once",
  #                               type_comment=="final Foil" ~ "Final Foil"))



# df_rt_pl_final =
  # df_pl %>% filter(task%in% c("finalTest")) %>% 
    # select(subject_id,  rt, condition, stimulusConditions, stimulusConditionName_nPlusOneTrial, listNum_appear0_initial,correct)

now=df_pl%>%filter(task=="detailSeenImages")
now$response

# ss=df_pl%>%filter(task=="surveyatend",subject_id=="6100434d983910e711b3a504")
# ss$response

df_pl%>%filter(subject_id=="67f909f80373c9f5af736a5a")

# show all accumulated accuracy
df_pl %>% group_by(subject_id)%>%filter(is_finished==1)%>%
  summarise(accmean=mean(all_accumulated_accuracy))

# show endsurvey Question answer
df_pl%>%filter(task=="surveyatend")%>%select(subject_id,response,accumulated_accuracy)

#present if they have seen images before
df_pl%>%filter(task%in%c("survey_HaveSeenImages","detailSeenImages"))%>%select(subject_id,HaveSeenImages,response,accumulated_accuracy)

#show if they once exited from full screen
df_pl %>% 
  filter(is_finished==1,subject_id!="",trial_index>=5,trial_index<1100)%>%
  group_by(subject_id)%>%
  summarize(wd = mean(width), ht=mean(height),is_changedfullscreen=mean(is_changedfullscreen))

df_pl%>%filter(subject_id=="6732ca9052a3b5780ec6068a")%>%select(width,height,trial_index)

#trial 1261 somehow detect different window size
df_pl%>%filter(subject_id=="6732ca9052a3b5780ec6068a")%>%select(width,height,trial_index, task,stimulus)%>%
  filter(height!=1080)
names(df_pl)

#see how many trials have rt>3500 in inital test
# 0.009826912 rate of NA response
#0.009826912 for that pass rt of 3500s
# 0.004913456 for that pass rt 3000

dhowmany = df_rt_pl%>%filter(task=="initialTest_response")%>%
  filter(!is.na(rt),rt>3000)
  # filter(is.na(rt))
dhowmany
dhowmany_base = df_rt_pl%>%filter(task=="initialTest_response")
dhowmany_base

length(dhowmany$task)/length(dhowmany_base$task)

df_pl%>%filter(subject_id=="67dc0e92b55a4d630f52e765")

d1ta = df_rt_pl%>%
  # filter(listNum_appear0_initial!=1 )%>%
# d1ta = df_pl2%>% 
  # filter(!is.na(rt),rt<3000)%>%
  mutate(colorskeme = case_when(current_assignmentTypesWithinList =="T_target" & is_currentObjAppear1=="true" ~"Target studied from current list",
                                is_currentObjAppear1=="false"  ~ paste("Foil from last trial",type_comment),
                                  current_assignmentTypesWithinList =="T_foil"  ~"Foil current list"))%>%
  filter(task=="initialTest_response")%>%
         group_by(task, condition, listNum_appear0_initial,colorskeme,subject_id)%>%
         summarise(cr = mean(correct))%>%
         group_by(task, condition, listNum_appear0_initial,colorskeme)%>%
         summarise(cr = mean(cr))%>%
  mutate(listNum_appear0_initial=as.factor(listNum_appear0_initial))
  # mutate(type_comment=as.factor(type_comment))
  
  
ggplot(data=d1ta)+
  geom_line(aes(x=listNum_appear0_initial, y= cr ,group=interaction(task,colorskeme),color= colorskeme,linetype=colorskeme))+ 
  geom_point(aes(x=listNum_appear0_initial,y=cr,group=interaction(task,colorskeme),color=colorskeme,shape=colorskeme),size =4 )+
  facet_grid(.~task)+
  scale_color_manual(values=c("blue","green","green","green","purple")) 

df_pl %>% filter(subject_id=="67acacf033444654db29a196")

# df_pl_combine%>%filter(codeversion==2)

df_rt_pl%>%group_by(subject_id)%>%
  summarize(n=n(), acc=mean(all_accumulated_accuracy))%>%
  arrange(acc)

combined_df%>%filter(subject_id=="6751acc5dc78128951a34f1f")%>%select(is_finished)
# c("6751acc5dc78128951a34f1f","67f909f80373c9f5af736a5a") #final acc =0.2...

# df_rt_pl%>%
```


```{r}
#correct treatment of rt
  df_pl %>% filter(task%in% c("initialTest_response","finalTest")) %>% 
  filter(is_finished==1)%>%
  filter(subject_id!="")%>%
  mutate(rt=as.numeric(rt))%>%
  filter(subject_id!="67ecdf3dcb59c5e0f274ad2d")%>%
  filter(is.na(rt)|rt>3000)%>%
  select(rt,subject_id,task)
  
#incorrect treatment of rt
    df_pl %>% filter(task%in% c("initialTest_response","finalTest")) %>% 
  filter(is_finished==1)%>%
      filter(subject_id!="")%>%
  # mutate(rt=as.numeric(rt))%>%
  filter(subject_id!="67ecdf3dcb59c5e0f274ad2d")%>%
  filter(is.na(rt)|rt>3000)%>%
      select(rt,subject_id)
    
    #original data after filter
    df_pl %>% filter(task%in% c("initialTest_response","finalTest")) %>% 
  filter(is_finished==1)%>%
      filter(subject_id!="")%>%
  # mutate(rt=as.numeric(rt))%>%
  filter(subject_id!="67ecdf3dcb59c5e0f274ad2d")
```

```{r}
dreal %>%
  # filter(is_finished==1)%>%
  filter(codeversion==2)%>%
  # mutate(subject_id=as.factor(subject_id))%>%
  group_by(subject_id)%>%
  # filter(Prolific)
  summarize(n=n())

# dreal$PROLIFIC_PID
c("67dc712c511053c8d90e2c29","67eac4d6bf3d1c4df7bd65df","67ed4e79983b8a8ba5517548")
```


## participant txt
```{r}

txtdf=combined_df %>%
  filter(is_finished==1)%>%
  filter(codeversion==2.3)%>%
  mutate(subject_id=as.factor(subject_id))%>%
  group_by(subject_id)%>%
  summarize(n=n(),all_accumulated_accuracy=mean(all_accumulated_accuracy))%>%
  ungroup()
txtdf
# txtdf%>%filter(subject_id!="67f909f80373c9f5af736a5a")
# txtdf%>%filter(subject_id=="673b60db7ecbdd53ec64a428")
df_pl %>%
  filter(is_finished==0)%>%
  group_by(PROLIFIC_PID)%>%
  summarize(nm=n())

df_pl%>% filter(PROLIFIC_PID=="67ecdf3dcb59c5e0f274ad2d")%>%
  group_by(recorded_at)%>%
  summarize(nm=n())

df_pl%>% filter(PROLIFIC_PID%in%c("67dc0e92b55a4d630f52e765","67d220de3ad5d3f4be7836bd","67c8eac5e82d76f9507e9534","67ecdf3dcb59c5e0f274ad2d"))%>%
  group_by(recorded_at,PROLIFIC_PID)%>%
  summarize(nm=n(),isf=mean(is_finished))

df_pltest %>%filter(PROLIFIC_PID=="67e8282387a710f6404aeb35")

# df_pl%>% filter(PROLIFIC_PID=="673b60db7ecbdd53ec64a428")


write.table(txtdf$subject_id, file = "output.txt", sep = "\t", row.names = FALSE, quote = FALSE)

# txtdf
# df_rt_pl$rt
# f2_aligned %>% select(subject_id)%>%
#   group_by(subject_id)%>%
#   summarize(n=n(), isf=mean(is_finished ))%>%
#   filter(subject_id=="67eb2ab3bd8cba1852857e2d")
# %>% filter(subject_id=="67eb2ab3bd8cba1852857e2d")

mt= read.csv(full_file_path_backup) 

mt %>%filter(subject_id=="6786cd9fca3e75e900edbd1c")%>%
  select(trial_index)%>%
  arrange(trial_index)

df_rt_pl%>%group_by(subject_id)%>%
  summarize(n=n())
```
## a complicated name check

```{r}
allapproved = txtdf$subject_id
inprolific = "
67eb2ab3bd8cba1852857e2d
5 May 2025, 01:52
00:42:00
COMPLETED

67e069199f5b036960b0cc5f
5 May 2025, 01:52
00:59:25
COMPLETED

67e9875c5b9b26c19a3bdf88
5 May 2025, 01:52
00:40:56
COMPLETED

678c0d73fea9aaf55cd880be
5 May 2025, 01:52
00:41:24
COMPLETED

63c1d184883ce15537788b40
5 May 2025, 01:52
01:20:50
COMPLETED

680ebf035ab59d342f31726e
5 May 2025, 01:52
00:47:42
NO CODE

673a27fe372ce97a95aecf5c
5 May 2025, 01:52
00:36:34
COMPLETED

6741ce8667002c96f0362d34
5 May 2025, 01:52
00:38:01
COMPLETED

67e8446d006a6c155f71bd2d
5 May 2025, 01:52
00:37:40
COMPLETED

66e8661e0c5e57cda7bf2d39
5 May 2025, 01:52
00:41:23
COMPLETED

6751acc5dc78128951a34f1f
5 May 2025, 01:52
00:31:24
COMPLETED

67eaf90db55644f3c56fffa9
5 May 2025, 01:53
00:40:12
COMPLETED

67e2fdf2d328f1e3dd7045b6
5 May 2025, 01:53
00:33:01
COMPLETED

67fff6438bb63725ca004b27
5 May 2025, 01:53
00:42:55
COMPLETED

67f05ce092cdcc0392692398
5 May 2025, 01:53
00:38:50
COMPLETED

67edb211a7c1d23c1535d6b2
5 May 2025, 01:53
00:45:54
COMPLETED

63268ad93b6ecc1acf782a21
5 May 2025, 01:53
00:33:08
COMPLETED

65c118f1cd19001157ace3a0
5 May 2025, 01:53
00:38:19
COMPLETED

5f9389fafdbecb173b329cca
5 May 2025, 01:55
00:35:27
COMPLETED

5fb39a485655aa025926ad30
67dc712c511053c8d90e2c29
2 May 2025, 19:46
00:47:58
COMPLETED

67ed4e79983b8a8ba5517548
2 May 2025, 19:46
00:38:29
COMPLETED

67eac4d6bf3d1c4df7bd65df
2 May 2025, 20:09
00:47:16
COMPLETED

67eefac7eaf3702ddd603092
3 May 2025, 22:25
01:16:36
COMPLETED

66cfb3d040139a5cfd914312
4 May 2025, 00:37
00:51:56
COMPLETED

67eade9122bddfb4cd165d09
4 May 2025, 20:06
00:40:03
COMPLETED

6767e3338fb21303557a8903
4 May 2025, 20:06
00:46:54
COMPLETED

67e4ae4138a215b586f1355c
4 May 2025, 20:06
00:43:44
COMPLETED

67c1a72590fcbf99458bb1f2
4 May 2025, 22:39
00:51:58
COMPLETED

6307f3c967020d1202332b77
4 May 2025, 22:40"

a_ids <- unlist(regmatches(inprolific, gregexpr("\\b[0-9a-f]{24}\\b", inprolific)))


write.table(a_ids[a_ids %in%allapproved], file = "output.txt", sep = "\t", row.names = FALSE, quote = FALSE)

extra_from_chat=c("673ccb0691efe91cd015dcf7","67558204d75dd7351fe9d17e","67dc0e92b55a4d630f52e765")

data_lost = c("67e4ae4138a215b586f1355c","6767e3338fb21303557a8903","67eade9122bddfb4cd165d09")

a_ids[!(a_ids %in%allapproved)& !(a_ids%in%data_lost)]#prolific approved list that is not in all_approvied list, and not datalost
# [1] "680ebf035ab59d342f31726e"


a_ids[!(allapproved %in%a_ids)] 
a_ids[!(a_ids %in%allapproved)]
txtdf%>%filter(subject_id=="67dc0e92b55a4d630f52e765")

names_from_backup=c("5f9389fafdbecb173b329cca", "5fb39a485655aa025926ad30", "6307f3c967020d1202332b77", 
  "63268ad93b6ecc1acf782a21", "63c1d184883ce15537788b40", "65c118f1cd19001157ace3a0", 
  "66cfb3d040139a5cfd914312", "66e8661e0c5e57cda7bf2d39", "673a27fe372ce97a95aecf5c", 
  "6741ce8667002c96f0362d34", "6751acc5dc78128951a34f1f", "67558204d75dd7351fe9d17e", 
  "678c0d73fea9aaf55cd880be", "67c1a72590fcbf99458bb1f2", "67dc0e92b55a4d630f52e765", 
  "67e069199f5b036960b0cc5f", "67e2fdf2d328f1e3dd7045b6", "67e8446d006a6c155f71bd2d", 
  "67e9875c5b9b26c19a3bdf88", "67eaf90db55644f3c56fffa9", "67eb2ab3bd8cba1852857e2d", 
  "67edb211a7c1d23c1535d6b2", "67eefac7eaf3702ddd603092", "67f05ce092cdcc0392692398", 
  "67fff6438bb63725ca004b27")

# names_from_backup[!(names_from_backup%in%allapproved)]
# the following are from proved list, but not in data and are not lost data for some reason
# [1] "680ebf035ab59d342f31726e" "67dc712c511053c8d90e2c29"
# [3] "67ed4e79983b8a8ba5517548" "67eac4d6bf3d1c4df7bd65df"
# d %>%filter(subject_id%in%c("67dc712c511053c8d90e2c29"))

dreal_er%>%filter(subject_id=="67dc712c511053c8d90e2c29")%>%
  filter(is_finished==1)
combined_df%>%filter(subject_id=="67dc712c511053c8d90e2c29")%>%
  filter(is_finished==1)
df_rt_pl%>%filter(subject_id=="67dc712c511053c8d90e2c29")
  # filter(is_finished==1)

combined_df %>%
  filter(is_finished==1)%>%
  # filter(codeversion==2)%>%
  mutate(subject_id=as.factor(subject_id))%>%
  group_by(subject_id)%>%
  summarize(n=n(),all_accumulated_accuracy=mean(all_accumulated_accuracy))%>%
  ungroup()
```




```{r}
# 5) columns in main_df but not in other_df (and vice versa)
main_cols  <- names(df_pl)
other_cols <- names(f2_aligned )
extra_in_main  <- setdiff(main_cols, other_cols)
extra_in_other <- setdiff(other_cols, main_cols)

extra_in_other
extra_in_main
df_pl[!(is.na(df_pl$rt_key_end)),]
df_pl%>%select(rt_key_end,rt_key_start, rt,rt_keypresses )%>%
  filter(complete.cases( rt_key_end,rt_keypresses,rt_key_start))
```

## final test

```{r}
ggplot(data=df_rt_pl)+
  geom_density(aes(x=rt,group=c(subject_id),color=subject_id))+
  facet_grid(task ~.)+
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")



d1t = df_rt_pl%>% 
  filter(task=="initialTest_response")%>%
         group_by(task,subject_id, condition,stimulusConditionName_nPlusOneTrial, listNum_appear0_initial)%>%
         summarise(cr = mean(correct))

# ggplot(data=d1t)+
#   geom_line(aes(x=listNum_appear0_initial, y= cr ,group=interaction(subject_id,task,stimulusConditionName_nPlusOneTrial ),color= stimulusConditionName_nPlusOneTrial))+ 
#   facet_grid(subject_id~task)+
#   theme(legend.position = "none")

d1t = df_rt_pl%>% 
 mutate(colorskeme = case_when(current_assignmentTypesWithinList =="T_target" & is_currentObjAppear1=="true" ~"Target studied from current list",
                                is_currentObjAppear1=="false"  ~ paste("Foil from last trial",type_comment),
                                  current_assignmentTypesWithinList =="T_foil"  ~"Foil current list"))%>%
  filter(task=="initialTest_response")%>%
         group_by(task, condition, listNum_appear0_initial,colorskeme,subject_id)%>%
         summarise(cr = mean(correct))%>%
  mutate(listNum_appear0_initial=as.factor(listNum_appear0_initial))
  # mutate(type_comment=as.factor(type_comment))

# ggplot(data=d1t)+
#    geom_line(aes(x=listNum_appear0_initial, y= cr ,group=interaction(task,colorskeme),color= colorskeme,linetype=colorskeme))+ 
#   geom_point(aes(x=listNum_appear0_initial,y=cr,group=interaction(task,colorskeme),color=colorskeme,shape=colorskeme),size =4 )+
#   facet_grid(subject_id~task)+
#   scale_color_manual(values=c("blue","green","green","green","purple"))+
#   theme(legend.position = "none")


d1t = df_rt_pl%>% 
 mutate(colorskeme = case_when(current_assignmentTypesWithinList =="T_target" & is_currentObjAppear1=="true" ~"Target studied from current list",
                                is_currentObjAppear1=="false"  ~ "Foil from last trial",
                                  current_assignmentTypesWithinList =="T_foil"  ~"Foil current list"))%>%
  filter(task=="initialTest_response")%>%
  filter(colorskeme=="Foil from last trial")%>%
         group_by(task, condition, listNum_appear0_initial,colorskeme,subject_id)%>%
         summarise(cr = mean(correct))%>%
  mutate(listNum_appear0_initial=as.factor(listNum_appear0_initial))
  # mutate(type_comment=as.factor(type_comment))

ggplot(data=d1t)+
   geom_line(aes(x=listNum_appear0_initial, y= cr ,group=interaction(task,colorskeme,subject_id),color= subject_id,linetype=colorskeme))+
  # geom_point(aes(x=listNum_appear0_initial,y=cr,group=interaction(task,colorskeme),color=colorskeme,shape=colorskeme),size =4 )+
  facet_grid(factor(as.numeric(as.factor(subject_id)) %/% 5) ~ task) +
  theme(legend.position = "none")
  
  # scale_color_manual(values=c("blue","green","purple"))

levels(as.factor(df_pl$codeversion ))
  
#   x=c(
# 152497,
# 154621,
# 156734,
# 158849,
# 160967,
# 163083,
# 165208
# )
# for (i in 1:length(x)){
#   if(i>=2){
#     print(x[i]-x[i-1])
#   }
# }
# x[2]-x[1]
mu=seq(0.1,5,by=0.01)
sigma1 = seq(0.01,0.09, by=0.01)
sigma2 = seq(1,2, by=0.01)
sigma3=seq(10,20,length.out=100)
plot(mu, mu/sigma1)
plot(mu, mu/sigma2)
plot(mu, mu/sigma3)
```



## avg initial result
 Use radiant's `radiant.plot` to display multiple plots in one chunk
library(radiant.plot)

 Create a list of plots
plots <- list(
  ggplot(data=d1ta) +
    geom_line(aes(x=listNum_appear0_initial, y=cr, group=interaction(task, colorskeme), color=colorskeme, linetype=colorskeme)) +
    geom_point(aes(x=listNum_appear0_initial, y=cr, group=interaction(task, colorskeme), color=colorskeme, shape=colorskeme), size=4) +
    facet_grid(. ~ task) +
    scale_color_manual(values=c("blue", "green", "green", "green", "purple")),

  ggplot(data=d1taf) +
    geom_line(aes(x=listNum_appear1_initial, y=cr, group=interaction(task, type_comment), color=type_comment, linetype=type_comment)) +
    geom_point(aes(x=listNum_appear1_initial, y=cr, group=interaction(task, type_comment), color=type_comment, shape=type_comment)) +
    facet_grid(. ~ task) +
    scale_color_manual(values=c("blue", "blue", "red", "green", "green", "purple", "purple"))
)


## dreal

```{r}
d1ta =
  f2_aligned%>%
filter(task%in% c("initialTest_response","finalTest")) %>% 
  filter(is_finished==1)%>%
  mutate(rt=as.numeric(rt))%>%
  # filter(subject_id!="67ecdf3dcb59c5e0f274ad2d")%>%
    filter(subject_id!="")%>%
  filter(!is.na(rt),rt<3000)%>%
      mutate(typecomment_in = case_when(current_assignmentTypesWithinList =="T_target" & is_currentObjAppear1=="true" ~"Target",
                                is_currentObjAppear1=="false" & type_comment=="current target, in next trial, from last trial"  ~ "Inherented Foil - Last Target",
                                                                is_currentObjAppear1=="false" & type_comment=="studied only, in next trial, from last trial"  ~ "Inherented Foil - Last Studied Only",
                                                                is_currentObjAppear1=="false" & type_comment=="tested only, in next trial, from last trial"  ~ "Inherented Foil - Last Foil",
                                
                                  current_assignmentTypesWithinList =="T_foil"  ~"New Foil"))%>%
  filter(!is.na(rt),rt<3000)%>%
  filter(task=="initialTest_response")%>%
  # mutate(colorskeme=type_comment)%>%
  mutate(colorskeme=typecomment_in)%>%
         group_by(task, condition, listNum_appear0_initial,colorskeme,subject_id)%>%
         summarise(cr = mean(correct)) %>%group_by(task, condition, listNum_appear0_initial,colorskeme)%>%
         summarise(cr = mean(cr))%>%
  mutate(listNum_appear0_initial=as.factor(listNum_appear0_initial))
  # mutate(type_comment=as.factor(type_comment))

#############################3PLOT
levelsStr = c("New Foil", "Target", "Inherented Foil - Last Foil" ,
             "Inherented Foil - Last Target" ,"Inherented Foil - Last Studied Only") 
ggplot(data=d1ta)+
  geom_line(aes(x=listNum_appear0_initial, y= cr ,group=interaction(task,colorskeme),color= colorskeme,linetype=colorskeme))+ 
  geom_point(aes(x=listNum_appear0_initial,y=cr,group=interaction(task,colorskeme),color=colorskeme,shape=colorskeme),size =4 )+
  facet_grid(.~task)+
  scale_color_manual(
  values = c("Inherented Foil - Last Foil" = "green", "Inherented Foil - Last Studied Only" = "green", "Inherented Foil - Last Target" = "green","New Foil" = "blue","Target"=  "purple"),
  breaks =  levelsStr# change order in legend
)+
  scale_shape_discrete(breaks=levelsStr)+
  scale_linetype_discrete(breaks=levelsStr)
```

```{r}
f2_aligned%>%group_by(subject_id)%>%
  summarize(n=n())
```





## *Display all plots
plot_all(plots)
```{r}
# library(radiant)
# library(radiant.plot)
# d1ta = df_rt_pl%>%
d1ta = df_rt_pl%>%
  # filter(subject_id%in%c("67dc712c511053c8d90e2c29","67eac4d6bf3d1c4df7bd65df","67ed4e79983b8a8ba5517548"))%>%
# d1ta = df_pl3%>%
  # filter(listNum_appear0_initial!=1 )%>%
# d1ta = df_pl2%>% 
  filter(!is.na(rt),rt<3000)%>%
  filter(task=="initialTest_response")%>%
  # mutate(colorskeme=type_comment)%>%
  mutate(colorskeme=typecomment_in)%>%
         group_by(task, condition, listNum_appear0_initial,colorskeme,subject_id)%>%
         summarise(cr = mean(correct))%>%
         group_by(task, condition, listNum_appear0_initial,colorskeme)%>%
         summarise(cr = mean(cr))%>%
  mutate(listNum_appear0_initial=as.factor(listNum_appear0_initial))
  # mutate(type_comment=as.factor(type_comment))
  
#   [1] "Inherented Foil - Last Foil"       
# [2] "Inherented Foil - Last Studied Only"
# [3] "Inherented Foil - Last Target"      
# [4] "New Foil"                           
# [5] "Target"
levelsStr = c("New Foil", "Target", "Inherented Foil - Last Foil" ,
             "Inherented Foil - Last Target" ,"Inherented Foil - Last Studied Only") 
############# Between list results
#######################################################
ggplot(data=d1ta)+
  geom_line(aes(x=listNum_appear0_initial, y= cr ,group=interaction(task,colorskeme),color= colorskeme,linetype=colorskeme))+ 
  geom_point(aes(x=listNum_appear0_initial,y=cr,group=interaction(task,colorskeme),color=colorskeme,shape=colorskeme),size =4 )+
  facet_grid(.~task)+
  scale_color_manual(
  values = c("Inherented Foil - Last Foil" = "green", "Inherented Foil - Last Studied Only" = "green", "Inherented Foil - Last Target" = "green","New Foil" = "blue","Target"=  "purple"),
  breaks =  levelsStr# change order in legend
)+
  scale_shape_discrete(breaks=levelsStr)+
  scale_linetype_discrete(breaks=levelsStr)


######################## Between list by listnum_appear2_initial
d1ta = df_rt_pl%>%
  # filter(listNum_appear0_initial!=1 )%>%
# d1ta = df_pl2%>% 
  # mutate(colorskeme = case_when(current_assignmentTypesWithinList =="T_target" & is_currentObjAppear1=="true" ~"Target studied from current list",
  #                               is_currentObjAppear1=="false"  ~ paste("Foil from last trial",type_comment),
  #                                 current_assignmentTypesWithinList =="T_foil"  ~"Foil current list"))%>%
  filter(task=="initialTest_response")%>%
         group_by(task, condition, listNum_appear2_initial,type_comment,subject_id)%>%
         summarise(cr = mean(correct))%>%
         group_by(task, condition, listNum_appear2_initial,type_comment)%>%
         summarise(cr = mean(cr))%>%
        mutate(listNum_appear2_initial=as.integer(listNum_appear2_initial))%>%
  filter(listNum_appear2_initial%in%2:10)
        
  # mutate(listNum_appear1_initial=as.factor(listNum_appear2_initial))
  # mutate(type_comment=as.factor(type_comment))
  

d1ta 

ggplot(data=d1ta)+
  geom_line(aes(x=listNum_appear2_initial, y= cr ,group=interaction(task,type_comment),color= type_comment,linetype=type_comment))+ 
  geom_point(aes(x=listNum_appear2_initial,y=cr,group=interaction(task,type_comment),color=type_comment,shape=type_comment),size =4 )+
  facet_grid(.~task)+scale_x_continuous(breaks=1:10)

# d1ta %>% filter(listNum_appear2_initial==2, type_comment=="current target, in next trial, from last trial" )
  # scale_color_manual(values=c("blue","green","green","green","purple"))
# levels(as.factor(df_rt_pl$type_comment ))
# ggplot(data=d1ta)+
#   geom_line(aes(x=listNum_appear0_initial, y= cr ,group=interaction(task,type_comment ),color= type_comment,linetype=type_comment))+ 
#   geom_point(aes(x=listNum_appear0_initial,y=cr,group=interaction(task,type_comment),color=type_comment))+
#   facet_grid(.~task)+
#   scale_color_manual(values=c("blue","green","blue","green","purple","green","purple"))

####################################### Within list by study position
d1ta = df_rt_pl%>% 
  filter(task=="initialTest_response")%>%
  mutate(type_comment = typecomment_in, studyPos_appear0_initial = as.numeric(studyPos_appear0_initial))%>%
  mutate(studyPos_appear0_initial = ceiling(studyPos_appear0_initial/3))%>%
         group_by(task, condition,type_comment, studyPos_appear0_initial,subject_id )%>%
  # mutate(studyPos_appear0_initial=as.numeric(studyPos_appear0_initial))%>%
  mutate(studyPos_appear0_initial=as.numeric(studyPos_appear0_initial))%>% #change here to see that by study or test position
         summarise(cr = mean(correct))%>%
           group_by(task, condition,type_comment, studyPos_appear0_initial )%>%
         summarise(cr = mean(cr))
  

ggplot(data=d1ta)+
  geom_line(aes(x=studyPos_appear0_initial, y= cr ,group=interaction(task,type_comment ),color= type_comment,linetype=type_comment))+ 
  geom_point(aes(x=studyPos_appear0_initial,y=cr,group=interaction(task,type_comment),shape=type_comment,color=type_comment),size=2)+
  facet_grid(.~task)+
  scale_color_manual(values=c("green","green","green","blue","purple"))



####################################### Within list by test position
d1ta = df_rt_pl%>% 
  filter(task=="initialTest_response")%>%
    mutate(type_comment = typecomment_in, testPos_appear0_initial =
             as.numeric(testPos_appear0_initial))%>%
  mutate(testPos_appear0_initial = ceiling(testPos_appear0_initial/3))%>%
         group_by(task, condition,type_comment, testPos_appear0_initial,subject_id )%>%
  # mutate(studyPos_appear0_initial=as.numeric(studyPos_appear0_initial))%>%
  mutate(testPos_appear0_initial=as.numeric(testPos_appear0_initial))%>% #change here to see that by study or test position
         summarise(cr = mean(correct))%>%
           group_by(task, condition,type_comment, testPos_appear0_initial )%>%
         summarise(cr = mean(cr))
  
ggplot(data=d1ta)+
  geom_line(aes(x=testPos_appear0_initial, y= cr ,group=interaction(task,type_comment ),color= type_comment,linetype=type_comment))+ 
  geom_point(aes(x=testPos_appear0_initial,y=cr,group=interaction(task,type_comment),shape=type_comment,color=type_comment))+
  facet_grid(.~task)+
  scale_color_manual(values=c("green","green","green","blue","purple"))

d1ta = df_rt_pl%>% 
  # filter(codeversion!=1)%>%
  filter(listNum_appear0_initial!=1 )%>%
  filter(task=="initialTest_response")%>%
    mutate(type_comment = case_when(current_assignmentTypesWithinList =="T_target" & is_currentObjAppear1=="true" ~"Target studied from current list",
                                is_currentObjAppear1=="false"  ~ paste("Foil from last trial",type_comment),
                                  current_assignmentTypesWithinList =="T_foil"  ~"Foil current list"))%>%
         group_by(task, condition,type_comment, testPos_appear0_initial,subject_id )%>%
         summarise(cr = mean(correct))%>%
           group_by(task, condition,type_comment, testPos_appear0_initial )%>%
         summarise(cr = mean(cr))%>%
  mutate(testPos_appear0_initial=as.numeric(testPos_appear0_initial))
  
# ggplot(data=d1ta)+
#   geom_line(aes(x=testPos_appear0_initial, y= cr ,group=interaction(task,type_comment ),color= type_comment,linetype=type_comment))+
#   geom_point(aes(x=testPos_appear0_initial,y=cr,group=interaction(task,type_comment),shape=type_comment,color=type_comment),size=5)+
#   facet_grid(.~task)
#   # scale_color_manual(values=c("blue","green","green","green","purple"))
# d1ta = df_rt_pl%>%
#   filter(codeversion!=1)%>%
#   filter(listNum_appear0_initial!=1 )%>%
#   filter(task=="initialTest_response")%>%
#     mutate(type_comment = case_when(current_assignmentTypesWithinList =="T_target" & is_currentObjAppear1=="true" ~"Target studied from current list",
#                                 is_currentObjAppear1=="false"  ~ paste("Foil from last trial",type_comment),
#                                   current_assignmentTypesWithinList =="T_foil"  ~"Foil current list"))%>%
#   mutate(testPos_appear0_initial=as.numeric(testPos_appear0_initial))%>%
#   mutate(ilgroup= case_when(listNum_appear0_initial > 5 ~1,
#                             TRUE~2) )%>%
#          group_by(task, condition,type_comment, testPos_appear0_initial,subject_id, ilgroup)%>%
#          summarise(cr = mean(correct))%>%
#            group_by(task, condition,type_comment, testPos_appear0_initial ,ilgroup)%>%
#          summarise(cr = mean(cr))%>%
#   mutate(testPos_appear0_initial=as.numeric(testPos_appear0_initial))
#   d1ta

# ggplot(data=d1ta)+
#   geom_line(aes(x=testPos_appear0_initial, y= cr ,group=interaction(task,type_comment,ilgroup ),color= type_comment,linetype=type_comment))+
#   geom_point(aes(x=testPos_appear0_initial,y=cr,group=interaction(task,type_comment,ilgroup),shape=type_comment,color=type_comment),size=2)+
#   facet_grid(task~ilgroup)


d1ta = df_rt_pl%>%
  # filter(listNum_appear0_initial!=1 )%>%
  filter(task=="initialTest_response")%>%
    mutate(type_comment = case_when(current_assignmentTypesWithinList =="T_target" & is_currentObjAppear1=="true" ~"Target studied from current list",
                                is_currentObjAppear1=="false"  ~ paste("Foil from last trial",type_comment),
                                  current_assignmentTypesWithinList =="T_foil"  ~"Foil current list"))%>%
  mutate(testPos_appear0_initial=as.numeric(testPos_appear0_initial))%>%
  mutate(ilgroup= listNum_appear0_initial)%>%
  # mutate(testPos_appear0_initial=as.numeric(testPos_appear0_initial))
  mutate(tsgroup= case_when(testPos_appear0_initial<=10 ~ 1,
                            testPos_appear0_initial<=20 & testPos_appear0_initial>10 ~ 2,
                             TRUE ~ 3))%>%
  filter(ilgroup<=6)%>%
         group_by(task, condition,type_comment, tsgroup,subject_id, ilgroup)%>%
         summarise(cr = mean(correct))%>%
           group_by(task, condition,type_comment, tsgroup ,ilgroup)%>%
         summarise(cr = mean(cr))
  d1ta

ggplot(data=d1ta)+
  geom_line(aes(x=tsgroup, y= cr ,group=interaction(task,type_comment,ilgroup ),color= type_comment,linetype=type_comment))+
  geom_point(aes(x=tsgroup,y=cr,group=interaction(task,type_comment,ilgroup),shape=type_comment,color=type_comment),size=2)+
  facet_grid(task~ilgroup)+
  scale_color_manual(values=c("blue","green","green","green","purple"))
```


/home/lea/Insync/naszhu@gmail.com/Google Drive/shulai@iu.edu 2022-09-04 14:28/IUB/Project-context
## avg final result

listNum_infinalOrder,listNum_appear1_initial, anRepeatedItem
[1] "Final Foil"                   
[2] "Foil(n), Foil (n+1)"          
[3] "Foil(n); Appear once"         
[4] "Studied-only (n); Appear once"
[5] "Studied-only (n); Foil (n+1)" 
[6] "Target: studied and tested at (n), Foil (n+1)"         
[7] "Target: : started and tested at (n) ; Appear once"    
```{r}
ds=df_rt_pl%>%filter(task=="finalTest")

levels(as.factor(ds$type_comment_fn))

df_pl%>% 
  filter(task=="finalTest")%>%
  # mutate(listNum_appear1_initial=as.numeric(listNum_infinalOrder),
  #        case_when(is.na(listNum_appear1_initial)~0,
  #                  TRUE ~ listNum_appear1_initial))%>%
  # mutate(type_comment=type_comment_fn)%>%
         group_by(task, condition,type_comment, listNum_appear1_initial)%>%
         summarize(n=n())


df_rt_pl %>% 
  filter(task=="finalTest")%>%
  # mutate(listNum_appear1_initial=as.numeric(listNum_infinalOrder),
  #        case_when(is.na(listNum_appear1_initial)~0,
  #                  TRUE ~ listNum_appear1_initial))%>%
  mutate(type_comment=type_comment_fn)%>%
         group_by(task, condition,type_comment, listNum_appear1_initial)%>%
         summarize(n=n())
df_rt_pl%>%
  group_by(subject_id)%>%
  summarize(n=n())
```


## final data for dreal only

only for firebase data

```{r}
levelsStr_fn = c("Target: studied and tested at (n), Foil (n+1)", 
                 "Studied-only (n); Foil (n+1)", 
             "Target: : started and tested at (n) ; Appear once" ,
             "Foil(n), Foil (n+1)",
             "Foil(n); Appear once", 
             "Studied-only (n); Appear once",
             "Final Foil"
)

d1taf = f2_aligned%>% 
    mutate(type_comment_fn=case_when(
                                stimulusConditions=="B"~
                                  "Target: : started and tested at (n) ; Appear once",
                                stimulusConditions == "Cn"~
                                  "Studied-only (n); Foil (n+1)",
                                stimulusConditions =="Dn" ~ 
                                  "Target: studied and tested at (n), Foil (n+1)",
                                stimulusConditions=="A"~
                                  "Studied-only (n); Appear once",
                                stimulusConditions=="Fnn"~
                                  "Foil(n), Foil (n+1)",
                                stimulusConditions=="Fn"~
                                  "Foil(n); Appear once",
                                stimulusConditions=="FF" ~
                                  "Final Foil"))%>%
  filter(task=="finalTest")%>%
  mutate(correct=case_when(correct=="True"~1,
                           correct=="False"~0,
                           TRUE ~ correct))%>%
  # mutate(listNum_appear1_initial=as.numeric(listNum_infinalOrder),
  #        case_when(is.na(listNum_appear1_initial)~0,
  #                  TRUE ~ listNum_appear1_initial))%>%
  mutate(type_comment=type_comment_fn)%>%
  # mutate(type_comment=type_comment)%>%
         group_by(task, condition,type_comment, listNum_appear1_initial, subject_id)%>%
         summarise(cr = mean(correct))%>%
         group_by(task, condition,type_comment, listNum_appear1_initial)%>%
         summarise(cr = mean(cr))%>%
  mutate(task=as.factor(task),type_comment=as.factor(type_comment))

# tag each row with its row number
d1taf_rows <- d1taf %>% mutate(row_id = row_number())

# find the “bad” ones
bad_points <- d1taf_rows %>%
  filter(
    is.na(listNum_appear1_initial) |    # missing x
    is.na(cr)                    |    # missing y
    !type_comment %in% levelsStr_fn      # shape would be NA
  )

if (nrow(bad_points) == 0) {
  cat("No rows will be dropped by geom_point().\n")
} else {
  cat("Rows dropped by geom_point():\n")
  print(bad_points)
}

ggplot(data=d1taf)+
  geom_line(aes(x=listNum_appear1_initial, y= cr ,group=interaction(task,type_comment ),color= type_comment,linetype=type_comment),size=1)+ 
  
    geom_point(aes(x=listNum_appear1_initial, y= cr ,group=interaction(task,type_comment ),color= type_comment,shape=type_comment),size=4)+ 
  facet_grid(.~task)+
  scale_color_manual(values=c("Target: studied and tested at (n), Foil (n+1)"="purple","Studied-only (n); Foil (n+1)"="green",
             "Target: : started and tested at (n) ; Appear once" ="purple",
             "Foil(n), Foil (n+1)" ="blue",
             "Foil(n); Appear once" ="blue",
             "Studied-only (n); Appear once" = "green",
             "Final Foil"="red" ),breaks=levelsStr_fn )+
  scale_shape_discrete(breaks=levelsStr_fn)+
  scale_linetype_discrete(breaks=levelsStr_fn)+
  theme(main="Final Teste by intial position chunk")
```

```{r}
f2_aligned %>% 
  filter(task=="finalTest")%>%
  # mutate(listNum_appear1_initial=as.numeric(listNum_infinalOrder),
  #        case_when(is.na(listNum_appear1_initial)~0,
  #                  TRUE ~ listNum_appear1_initial))%>%
  # mutate(type_comment=type_comment_fn)%>%
         group_by(task, condition,type_comment, listNum_appear1_initial, subject_id)%>%
         summarise(cr = mean(correct))%>%
         group_by(task, condition,type_comment, listNum_appear1_initial)%>%
         summarise(cr = mean(cr))
```

c("Target: studied and tested at (n), Foil (n+1)", 
                 "Studied-only (n); Foil (n+1)", 
             "Target: : started and tested at (n) ; Appear once" ,
             "Foil(n), Foil (n+1)",
             "Foil(n); Appear once", 
             "Studied-only (n); Appear once",
             "Final Foil"
)
## *FINAL plot 
```{r,fig.width=8, fig.height=5}
levelsStr_fn = levels(as.factor(df_rt_pl$type_comment_fn))

############ First plot

d1taf = df_rt_pl%>% 
  mutate(correct=case_when(correct=="True"~1,
                           correct=="False"~0,
                           TRUE ~ correct))%>%
  filter(task=="finalTest")%>%
  # mutate(listNum_appear1_initial=as.numeric(listNum_infinalOrder),
  #        case_when(is.na(listNum_appear1_initial)~0,
  #                  TRUE ~ listNum_appear1_initial))%>%
  mutate(type_comment=type_comment_fn)%>%
         group_by(task, condition,type_comment, listNum_appear1_initial, subject_id)%>%
         summarise(cr = mean(correct))%>%
         # summarise(cr = median(correct))%>%
         group_by(task, condition,type_comment, listNum_appear1_initial)%>%
         summarise(cr = mean(cr))

# 2. identify the rows that will be dropped by geom_point()
dropped <- d1taf %>%
  mutate(row_id = row_number()) %>%
  filter(
    is.na(listNum_appear1_initial) |   # missing x
    is.na(cr)                     |   # missing y
    !type_comment %in% levelsStr_fn     # not covered by your manual scales
  )

cat("Rows dropped due to missing values:\n")
print(dropped)

ggplot(data=d1taf)+
  geom_line(aes(x=listNum_appear1_initial, y= cr ,group=interaction(task,type_comment ),color= type_comment,linetype=type_comment),size=1)+ 
  
    geom_point(aes(x=listNum_appear1_initial, y= cr ,group=interaction(task,type_comment ),color= type_comment,shape=type_comment),size=4)+ 
  facet_grid(.~task)+ 
  scale_color_manual(values=c("Target: studied and tested at (n), Foil (n+1)"="purple","Studied-only (n); Foil (n+1)"="green", 
             "Target: : started and tested at (n) ; Appear once" ="purple",
             "Foil(n), Foil (n+1)" ="blue",
             "Foil(n); Appear once" ="blue", 
             "Studied-only (n); Appear once" = "green",
             "Final Foil"="red" ),breaks=levelsStr_fn )+
  scale_shape_discrete(breaks=levelsStr_fn)+
  scale_linetype_discrete(breaks=levelsStr_fn)+
  theme(main="Final Teste by intial position chunk")

############ second plot
d1taf = df_rt_pl%>% 
    mutate(correct=case_when(correct=="True"~1,
                           correct=="False"~0,
                           TRUE ~ correct))%>%
  filter(task=="finalTest")%>%
  # mutate(listNum_appear1_initial=as.numeric(listNum_infinalOrder),
  #        case_when(is.na(listNum_appear1_initial)~0,
  #                  TRUE ~ listNum_appear1_initial))%>%
  mutate(type_comment=type_comment_fn)%>%
         group_by(task, condition,type_comment, listNum_infinalOrder, subject_id)%>%
         summarise(cr = mean(correct))%>%
         group_by(task, condition,type_comment, listNum_infinalOrder)%>%
         summarise(cr = mean(cr))%>%
  mutate(listNum_infinalOrder=as.integer(listNum_infinalOrder))


ggplot(data=d1taf)+
  geom_line(aes(x=listNum_infinalOrder, y= cr ,group=interaction(task,type_comment ),color= type_comment,linetype=type_comment),size=1)+ 
    geom_point(aes(x=listNum_infinalOrder, y= cr ,group=interaction(task,type_comment ),color= type_comment,shape=type_comment),size=4)+ 
  facet_grid(.~task)+ 
  scale_color_manual(values=c("Target: studied and tested at (n), Foil (n+1)"="purple","Studied-only (n); Foil (n+1)"="green", 
             "Target: : started and tested at (n) ; Appear once" ="purple",
             "Foil(n), Foil (n+1)" ="blue",
             "Foil(n); Appear once" ="blue", 
             "Studied-only (n); Appear once" = "green",
             "Final Foil"="red" ),breaks=levelsStr_fn )+
  scale_shape_discrete(breaks=levelsStr_fn)+
  scale_linetype_discrete(breaks=levelsStr_fn)+
  theme(main="Final Teste by test position chunk")


################33 Within plot 1
d1taf2 = df_rt_pl%>% 
    mutate(correct=case_when(correct=="True"~1,
                           correct=="False"~0,
                           TRUE ~ correct))%>%
  mutate(type_comment=type_comment_fn)%>%
  mutate(testPos_appear1_initial=as.numeric(testPos_appear1_initial),testPos_appear1_initial=ceiling(testPos_appear1_initial/3))%>%
  
  filter(task=="finalTest")%>%
         group_by(task, condition,type_comment, testPos_appear1_initial )%>%
         summarise(cr = mean(correct))

ggplot(data=d1taf2)+
  geom_line(aes(x=testPos_appear1_initial, y= cr ,group=interaction(task,type_comment ),color= type_comment,linetype=type_comment))+ 
    geom_point(aes(x=testPos_appear1_initial, y= cr ,group=interaction(task,type_comment ),color= type_comment,shape=type_comment),size=5)+
  ylim(c(0.5,1))+
  scale_color_manual(values=c("Target: studied and tested at (n), Foil (n+1)"="purple","Studied-only (n); Foil (n+1)"="green", 
             "Target: : started and tested at (n) ; Appear once" ="purple",
             "Foil(n), Foil (n+1)" ="blue",
             "Foil(n); Appear once" ="blue", 
             "Studied-only (n); Appear once" = "green",
             "Final Foil"="red" ),breaks=levelsStr_fn )+
  facet_grid(.~task)

##############################
###########3 Within plot 2, by initial studyPos_appear1_initial
d1taf = df_rt_pl%>% 
  filter(task=="finalTest")%>%
  mutate(type_comment=type_comment_fn)%>%
    mutate( listNum_infinalOrder=as.numeric(studyPos_appear1_initial),listNum_infinalOrder=ceiling(listNum_infinalOrder/3))%>%
         group_by(task, condition,type_comment, listNum_infinalOrder)%>%
         summarise(cr = mean(correct))
  # mutate(type_comment=case_when(type_comment=="current target, in next trial" ~ "Target_n, Foil n+1",
  #                               type_comment=="current target, not in next trial"~
  #                                 "Target_n only",
  #                               type_comment == "studied only, in next trial"~
  #                                 "Studied-only n, foil n+1",
  #                               type_comment=="studied only, not in trial"~
  #                                 "Studied-only n only",
  #                               type_comment=="tested only, in next trial"~
  #                                 "Foil n, foil n+1",
  #                               type_comment=="tested only, not in next trial"~
  #                                 "Foil n only",))

ggplot(data=d1taf)+
  geom_line(aes(x=listNum_infinalOrder, y= cr ,group=interaction(task,type_comment ),color= type_comment,linetype=type_comment))+ 
    geom_point(aes(x=listNum_infinalOrder, y= cr ,group=interaction(task,type_comment ),color= type_comment,shape=type_comment),size=5)+ 
  facet_grid(.~task)+ 
  ylim(c(0.5,1))+

  scale_color_manual(values=c("Target: studied and tested at (n), Foil (n+1)"="purple","Studied-only (n); Foil (n+1)"="green", 
             "Target: : started and tested at (n) ; Appear once" ="purple",
             "Foil(n), Foil (n+1)" ="blue",
             "Foil(n); Appear once" ="blue", 
             "Studied-only (n); Appear once" = "green",
             "Final Foil"="red" ),breaks=levelsStr_fn )


```
```{r}
names(df_rt_pl)%>%
```



# df_pl_with_init
```{r}
df_pl%>%
  filter(is_finished==1)%>%
  mutate(correct=case_when(correct=="True"~1,
                           correct=="False"~0,
                           TRUE ~ correct))%>%
  filter(task=="finalTest")%>%
  mutate(correct_appear1=case_when(correct_appear1=="true"~1,
                                   correct_appear1=="false"~0,
                                   TRUE ~ 999) )%>%
  filter(stimulusConditions %in% c("Cn","Dn","Fnn") & listNum_appear1_initial!=10)%>%
  select(task,condition,type_comment,stimulusConditions ,correct_appear1,correct_appear2,listNum_appear1_initial)

### Below assign intialScore to finalT
initial_scores <-
  # df_rt_pl %>%
  df_rt_pl %>%
  filter(task == "initialTest_response") %>% 
  filter(!(stimulusConditionName_nPlusOneTrial=="Cn+1" & listNum_appear0_initial!=10), #those appear first time for study only
         !(stimulusConditionName_nPlusOneTrial=="Dn+1" & listNum_appear1_initial!=10),
         !(stimulusConditionName_nPlusOneTrial=="Fnn+1" & listNum_appear1_initial!=10)
         )%>% #have checked, after this step, each id_pic is unique for each sub, so don't worry below first()
  group_by(subject_id, id_picName) %>% 
  summarize(
    correct_appear1 = first(correct_appear1),
    correct_appear2 = first(correct_appear2),
    listNum_appear1_initial = first(listNum_appear1_initial),
    listNum_appear2_initial = first(listNum_appear2_initial),
    .groups = "drop"
  )

#double check to make sure unique appears , need to assign initail_scores for the lines before (group_by)
# initial_scores %>%
#   group_by(subject_id, id_picName) %>%
#   mutate(n=n())%>%
#   filter(n > 1) %>%
#   select(subject_id,id_picName,stimulusConditions, stimulusConditionName_nPlusOneTrial,listNum_appear1_initial,listNum_appear2_initial,n)

df_pl_with_init <-
# 0.009 (~1% data deon'st have initial score, prob they all are those that didn't have an rt (null)
  df_rt_pl %>%
  filter(task=="finalTest")%>%
    select(-correct_appear1,-correct_appear2, -listNum_appear1_initial, -listNum_appear2_initial)%>%
    # select(-correct_appear1,-correct_appear2)%>%
  left_join(initial_scores, by = c("subject_id","id_picName")) #%>%

```

```{r}
# df2%>%select(group_init,n_tests,correct_appear1,correct_appear2,probe_history, init_outcome, group_init)
# df2%>%select(group_init,n_tests)
```

## Joint Prob Plot
```{r}
df2 <-
  df_pl_with_init %>%
  ################# 1) single vs. two-test, only treat both appear to be n_tests=2
  #   Even though this will actually make SOn list num i but actually tested i+1 
  mutate(n_tests = if_else(correct_appear2=="null" | correct_appear1=="null", 1, 2)) %>%
  mutate(n_tests = if_else(is.na(correct_appear2) & is.na(correct_appear1), 0, n_tests)) %>%
  ################# 2) bin by initial list
  mutate(group_init = case_when(
    listNum_appear1_initial == 1        ~ "List1", #SO would be assigned here as well
    listNum_appear1_initial %in% 2:5    ~ "A (2–5)",
    listNum_appear1_initial %in% 6:9    ~ "B (6–9)",
    listNum_appear1_initial == 10       ~ "List10",
    listNum_appear1_initial == 0       ~  "FF", #final target no list
    # n_tests == 0        ~ "None List Exist" # no prior
  )) %>%
  ################### Add by final test
    mutate(group_finial = case_when(
    listNum_infinalOrder == 1        ~ "List1", #SO would be assigned here as well
    listNum_infinalOrder %in% 2:5    ~ "A (2–5)",
    listNum_infinalOrder %in% 6:9    ~ "B (6–9)",
    listNum_infinalOrder == 10       ~ "List10"
    # listNum_infinalOrder == 0       ~  "FF", #final target no list
    # n_tests == 0        ~ "None List Exist" # no prior
  )) %>%
  
  mutate(group_init = fct_relevel(group_init,
                                  "List1", "A (2–5)", "B (6–9)", "List10"))%>%
  ##rearrange factor level
  ################# 3) probe_history:
  mutate(
    probe_history = case_when(
      (n_tests == 1) & (stimulusConditions %in% c("Cn")) ~   "SOn: studied_only(~n)->foil(n+1)",
      (n_tests == 1) & (stimulusConditions %in% c("Fn")) ~       "F: new foil",
      (n_tests == 1) & (stimulusConditions %in% c("B"))       ~   "T: new target", 
      (n_tests == 2) & (stimulusConditions %in% c("Fnn"))     ~   "Fn: foil(n)->foil(n+1)",
      (n_tests == 2) & (stimulusConditions %in% c("Dn"))     ~   "Tn: target(n)->foil(n+1)",
      (n_tests == 0) & (stimulusConditions %in% c("A"))      ~   "SO: studied only(~n), no test", 
      (n_tests == 0) & (stimulusConditions %in% c("FF"))      ~   "FF: final New Foil",
      # type SO would not have a test, case SO (i.e., A) is ignored
    ),
    ################# 4) outcome:
    init_outcome = case_when(
      #either correct works becuase previously made sure only one of them is not NA
      n_tests == 1 & (correct_appear1 == "true" | correct_appear2 == "true") ~ "C", 
      n_tests == 1 & (correct_appear1 == "false" | correct_appear2 == "false") ~ "E",
      n_tests == 2 ~ paste0(
        if_else(correct_appear1=="true", "C1","E1"),
        "&",
        if_else(correct_appear2=="true", "C2","E2")
      ),
      n_tests == 0 ~ "No Init Outcome" #doesn't have a test(outcome) initially
    ),
    # define which column is your "final" accuracy
    correct_final = correct #correct rate final acc (numeric val 1 or 2)
  )
  ################# ⬅ EDIT 1: new factor for facet rows; but this is actually unused, could be discarded
  # mutate(
  #   newfac = case_when(
  #     probe_history %in% c("2.Fn: foil(n)->foil(n+1))")   ~ "Fn",
  #     probe_history %in% c("2.Tn: target(n)->foil(n+1)") ~ "Tn",
  #     TRUE ~ probe_history
  #   ) 
  # )
  # 3) remove the rows that are not needed
  # filter(!(group_init %in% c("List1","List 10") & n_tests==2) )

# 2) Aggregate ----------------------------------------------------------
agg <- df2 %>%
  pivot_longer(cols=c(group_init,group_finial),names_to="orderBy",values_to="group_init")%>%
  mutate(orderBy = if_else(orderBy=="group_init", "Initial Test Order", "Final Test Order"))%>%
  group_by(n_tests, group_init, probe_history, init_outcome, orderBy,subject_id ) %>% #new fac add or not addhere
   summarize(
    prob_final = mean(correct_final, na.rm=TRUE),
    .groups = "drop"
  )%>%
  group_by(n_tests, group_init, probe_history, init_outcome, orderBy ) %>% #new fac add or not addhere
  summarize(
    prob_final = mean(prob_final, na.rm=TRUE),
    .groups = "drop"
  )%>%
  # mutate(group_init = case_when(is.na(group_init)~"NAs",
  #                               TRUE ~ group_init),
  #        probe_history = case_when(is.na(probe_history)~"NAs",
  #                               TRUE ~ probe_history))%>%
  filter(complete.cases(group_init) & complete.cases(probe_history), complete.cases(init_outcome))%>% #to keep linetype detect
  mutate(group_init=as.factor(group_init), probe_history=as.factor(probe_history),init_outcome=as.factor(init_outcome),
         n_tests=as.factor(n_tests))%>%
  filter(!(group_init %in% c("List1","List10")))

# 5)########################33 plot
ggplot(agg, aes(x = group_init, y = prob_final,
               group    = interaction(init_outcome, probe_history))    ## EDIT: removed n_tests
     )+     ## EDIT ⬅)) +
  geom_line(aes(group    = interaction(init_outcome, probe_history),    ## EDIT: removed n_tests
               color    = interaction(n_tests, init_outcome),
               linetype = interaction(n_tests, init_outcome))
               ) +
  geom_point(aes(group    = interaction(init_outcome, probe_history),    ## EDIT: removed n_tests
               color    = interaction(n_tests, init_outcome),
               shape    = interaction(n_tests, init_outcome)),size=3) +
  facet_grid( orderBy ~ n_tests+probe_history,
             labeller = labeller(n_tests = c(`1`="Tested once", `2`="Tested twice"))) +
  labs(
    x = "Initial-list bin",
    y = "P(final correct)",
    # color = "Outcome",
    title = "Final Test performance by initial-list and final-list bin",
  ) + theme(legend.position = "bottom")
  # scale_color_manual(
  #   values = c(
  #     # for Tested once (n_tests = 1), map C & E to two colors:
  #     "1.C"   = "steelblue",
  #     "1.E"   = "firebrick",
  #     # for Tested twice (n_tests = 2), re-use those same two,
  #     # then assign two more for the other 2 outcomes:
  #     "2.C1&C2" = "steelblue",
  #     "2.C1&E2" = "firebrick",
  #     "2.E1&C2" = "darkgreen",
  #     "2.E1&E2" = "goldenrod"
  #   )
  # ) + 
  # scale_linetype_manual(
  #   values = c(
  #     # for Tested once:
  #     "1.F: new foil"                 = "solid",
  #     "1.T: new target"               = "longdash",
  #     "1.SOn: studied_only(~n)->foil(n+1)"= "solid",
  #     # for Tested twice:
  #     "2.Fn: foil(n)->foil(n+1)"   = "solid",
  #     "2.Tn: target(n)->foil(n+1)" = "dotted"
  #   )
  # )
  # theme_minimal()
# <!-- ``` -->

```


### Joint prob plot by group

```{r}
# df2 inital factor assign------------------
df2 <-
  df_pl_with_init %>%
  ################# 1) single vs. two-test, only treat both appear to be n_tests=2
  #   Even though this will actually make SOn list num i but actually tested i+1 
  mutate(n_tests = if_else(correct_appear2=="null" | correct_appear1=="null", 1, 2)) %>%
  mutate(n_tests = if_else(is.na(correct_appear2) & is.na(correct_appear1), 0, n_tests)) %>%
  ################# 2) bin by initial list
  mutate(group_init = case_when(
    listNum_appear1_initial == 1        ~ "List1", #SO would be assigned here as well
    listNum_appear1_initial %in% 2:5    ~ "A (2–5)",
    listNum_appear1_initial %in% 6:9    ~ "B (6–9)",
    listNum_appear1_initial == 10       ~ "List10",
    listNum_appear1_initial == 0       ~  "FF", #final target no list
    # n_tests == 0        ~ "None List Exist" # no prior
  )) %>%
  ################### Add by final test
    mutate(group_finial = case_when(
    listNum_infinalOrder == 1        ~ "List1", #SO would be assigned here as well
    listNum_infinalOrder %in% 2:5    ~ "A (2–5)",
    listNum_infinalOrder %in% 6:9    ~ "B (6–9)",
    listNum_infinalOrder == 10       ~ "List10"
    # listNum_infinalOrder == 0       ~  "FF", #final target no list
    # n_tests == 0        ~ "None List Exist" # no prior
  )) %>%
  
  mutate(group_init = fct_relevel(group_init,
                                  "List1", "A (2–5)", "B (6–9)", "List10"))%>%
  ##rearrange factor level
  ################# 3) probe_history:
  mutate(
    probe_history = case_when(
      (n_tests == 1) & (stimulusConditions %in% c("Cn")) ~   
        "SOn: studied_only(~n)->foil(n+1)",
      (n_tests == 1) & (stimulusConditions %in% c("Fn")) ~       
        "F: new foil",
      (n_tests == 1) & (stimulusConditions %in% c("B"))       ~   
        "T: new target", 
      (n_tests == 2) & (stimulusConditions %in% c("Fnn"))     ~   
        "Fn: foil(n)->foil(n+1)",
      (n_tests == 2) & (stimulusConditions %in% c("Dn"))     ~   
        "Tn: target(n)->foil(n+1)",
      (n_tests == 0) & (stimulusConditions %in% c("A"))      ~   
        "SO: studied only(~n), no test", 
      (n_tests == 0) & (stimulusConditions %in% c("FF"))      ~   
        "FF: final New Foil",
      # type SO would not have a test, case SO (i.e., A) is ignored
    ),
    ################# 4) outcome:
    init_outcome = case_when(
      #either correct works becuase previously made sure only one of them is not NA
      n_tests == 1 & (correct_appear1 == "true" | correct_appear2 == "true") ~ "C", 
      n_tests == 1 & (correct_appear1 == "false" | correct_appear2 == "false") ~ "E",
      n_tests == 2 ~ paste0(
        if_else(correct_appear1=="true", "C1","E1"),
        "&",
        if_else(correct_appear2=="true", "C2","E2")
      ),
      n_tests == 0 ~ "No Init Outcome" #doesn't have a test(outcome) initially
    ),
    # define which column is your "final" accuracy
    correct_final = correct #correct rate final acc (numeric val 1 or 2)
  )
  ################# ⬅ EDIT 1: new factor for facet rows; but this is actually unused,

# 2) Get single sub data----------------------------
DF_by_sub = df2 %>%
  pivot_longer(cols=c(group_init,group_finial),names_to="orderBy",values_to="group_init")%>%
  mutate(orderBy = if_else(orderBy=="group_init", "Initial Test Order", "Final Test Order"))%>%
  ##### (a) first sumamrize by detail & subject_id
  group_by(n_tests, group_init, probe_history, init_outcome, orderBy,subject_id  ) %>% #new fac add or not addhere
   summarize(
     mean_perf = mean(correct_final, na.rm=TRUE),
    .groups = "drop"
  )

# 3) get DF_rank ----------------------------------------------------------

DF_rank = DF_by_sub %>% # the dataset with a subject in each group as a row
  
  ###### (b) ADD rank groups below; performance_group
  ## performance group could be seen as subgroup of subj_id.?
  group_by(subject_id)%>% #just calc median for whole data for a single Ss
  summarize(sub_score_each = mean(mean_perf, na.rm=TRUE)) %>%
  arrange(sub_score_each) %>%
  mutate(rank_id =1:n() )%>%
  mutate(median_rank = median(rank_id))%>%
  # split into Low vs. High based on that threshold
  mutate( # have double checked soly, this is a good correct half-half seperation
    performance_group = if_else(rank_id <= median_rank, 
                         "Low rank (<= "  %>% paste0(median_rank) %>% paste0(")"),
                         "High rank (> "  %>% paste0(median_rank) %>% paste0(")"))
  ) 


# 4) get agg ############----------------------------------------------

agg <- DF_by_sub %>%
  left_join(DF_rank, by="subject_id")%>%
  # group_by(n_tests, group_init, probe_history, init_outcome, orderBy ) %>%
  group_by(n_tests, group_init, probe_history, init_outcome, orderBy,performance_group ) %>% #new fac add or not addhere
  summarize(
    prob_final = mean(mean_perf, na.rm=TRUE),
    .groups = "drop"
  )%>%
  # (d) add avg line
  # mutate(prob_final=mean_perf)%>%
  filter(complete.cases(group_init) & complete.cases(probe_history), complete.cases(init_outcome))%>% #to keep linetype detect
  group_by(n_tests, group_init, probe_history, init_outcome, orderBy ) %>% #new fac add or not addhere
  mutate(avg_score = mean(prob_final, na.rm=TRUE))%>%
  # rest work
  mutate(group_init=as.factor(group_init), probe_history=as.factor(probe_history),init_outcome=as.factor(init_outcome),
         n_tests=as.factor(n_tests))%>%
  filter(!(group_init %in% c("List1","List10"))) %>%
  ##rearrage factor
  mutate(interact = interaction(n_tests, init_outcome))%>%
  mutate(
    interact = factor(
      interact,
      levels = c(
        "1.C",      # first level
        "2.C1&C2",
        "2.C1&E2", # etc.
        "1.E",      # second
        "2.E1&C2",
        "2.E1&E2",
        "0.No Init Outcome"
      )
    ))



# 5) plot #---------------------------------------
ggplot(agg, aes(x = group_init, y = prob_final,
               group    = interaction(init_outcome, probe_history))    ## EDIT: removed n_tests
     )+     ## EDIT ⬅)) +
    # geom_line(aes(x=group_init, y=avg_score, group = interaction(init_outcome, probe_history),    ## EDIT: removed n_tests
    #            linetype = init_outcome), color    = "black"
    #            ) +
  geom_line(aes(group    = interaction(init_outcome, probe_history),    ## EDIT: removed n_tests
               color    = interact,
               linetype = interact)
               ) +
  geom_point(aes(group    = interaction(init_outcome, probe_history),    ## EDIT: removed n_tests
               color    = interact,
               shape    = interact),size=3) +
  facet_grid( orderBy+performance_group ~ n_tests+probe_history,
  # facet_grid( orderBy ~ n_tests+probe_history,
             labeller = labeller(n_tests = c(`1`="Tested once", `2`="Tested twice"))) +
  labs(
    x = "Initial-list bin",
    y = "P(final correct)",
    # color = "Outcome",
    title = "Final Test performance by initial-list and final-list bin",
  ) + theme(legend.position = "bottom")
```




## FINAL combined
```{r}
levelsStr_fn = levels(as.factor(df_rt_pl$type_comment_fn))

############ Plot for that in final order
#all types: Cn=0-1, Dn=1-1, Fnn=1-1, Fn=1-0, A=0-0, B=1-0

df_finalFoil_toappend = df_pl_with_init%>% 
  mutate(correct=case_when(correct=="True"~1,
                           correct=="False"~0,
                           TRUE ~ correct))%>%
  filter(task=="finalTest",stimulusConditions=="FF")%>%
  mutate(type_comment="Final F" ) %>%
  mutate(correct_appear_label = " Final Foil")%>%
  mutate(init_outcome = 999)%>% #first or second time in initail correct =0 becuase didn't appear
  select(task, condition,type_comment, listNum_infinalOrder, subject_id,init_outcome,correct_appear_label, correct)

d1taf = df_pl_with_init%>%
  mutate(correct=case_when(correct=="True"~1,
                           correct=="False"~0,
                           TRUE ~ correct))%>%
  filter(task=="finalTest")%>%
  mutate(correct_appear1=case_when(correct_appear1=="true"~1,
                                   correct_appear1=="false"~0,
                                   TRUE ~ 5 ) )%>%
    mutate(correct_appear2=case_when(correct_appear2=="true"~1,
                                   correct_appear2=="false"~0,
                                   TRUE ~ 5 ) )%>%
  mutate(type_comment = "Final T" )%>% #these are all final targets
  pivot_longer(cols=c(correct_appear1,correct_appear2),names_to="correct_appear_label",values_to="init_outcome")%>%
    # mutate(listNum_appear1_initial=listNum_appear1_initial)%>%
  select(task, condition,type_comment, listNum_infinalOrder, subject_id,init_outcome,correct_appear_label,correct)%>%
  #bind rows from df_finalFoil_toappend
  bind_rows(df_finalFoil_toappend)%>%
  mutate(correct_appear_label=case_when(correct_appear_label=="correct_appear1"~"Target - by first appearance correction",
                                        correct_appear_label=="correct_appear2"~"Target - by second appearance correction",
                                        TRUE ~ correct_appear_label) )%>%
  filter(init_outcome!=5)%>% #take away the null for correct_appear both
  mutate(correct_appear1=init_outcome)%>%
  mutate(correct_appear1=case_when(correct_appear1==1~"Corrected Initial",
                                        correct_appear1==0 ~ "Wrong Initial",
                                   correct_appear1==999 ~"[Final FOIL initial not appear]",
                                        TRUE ~ "MISS") )%>%
  # mutate(listNum_appear1_initial=listNum_appear1_initial)%>%
  mutate(listNum_appear1_initial=listNum_infinalOrder)%>%
  # filter(type_comment_fn=="Target: : started and tested at (n) ; Appear once")%>%
  # mutate(listNum_appear1_initial=as.numeric(listNum_infinalOrder),
  #        case_when(is.na(listNum_appear1_initial)~0,
  #                  TRUE ~ listNum_appear1_initial))%>%
  # mutate(type_comment=type_comment_fn)%>%
         group_by(task, condition,type_comment, listNum_appear1_initial, subject_id,correct_appear1,correct_appear_label)%>%
         summarise(cr = mean(correct),se_cr = sd(correct,na.rm = TRUE) / sqrt(n()))%>%
         group_by(task, condition,type_comment, listNum_appear1_initial,correct_appear1,correct_appear_label)%>%
         summarise(cr = mean(cr), se_cr = mean(se_cr))%>%
  mutate(correct_appear1=as.factor(correct_appear1),correct_appear_label=as.factor(correct_appear_label))%>%
  mutate(listNum_appear1_initial=as.integer(listNum_appear1_initial))



ggplot(data=d1taf)+
  geom_line(aes(x=listNum_appear1_initial, y= cr ,group=interaction(task,type_comment,correct_appear1,correct_appear_label ),color= type_comment,linetype=correct_appear1),size=1)+ 
  
    geom_point(aes(x=listNum_appear1_initial, y= cr ,group=interaction(task,type_comment,correct_appear1,correct_appear_label  ),color= type_comment,shape=correct_appear1),size=4)+ 
  facet_grid(.~task)+ 
  # scale_color_manual(values=c("Target: studied and tested at (n), Foil (n+1)"="purple","Studied-only (n); Foil (n+1)"="green", 
  #            "Target: : started and tested at (n) ; Appear once" ="purple",
  #            "Foil(n), Foil (n+1)" ="blue",
  #            "Foil(n); Appear once" ="blue", 
  #            "Studied-only (n); Appear once" = "green",
  #            "Final Foil"="red" ),breaks=levelsStr_fn )+
  # scale_shape_discrete(breaks=levelsStr_fn)+
  # scale_linetype_discrete(breaks=levelsStr_fn)+
  #set x axis break to be descrete 1-10
  scale_x_continuous(breaks=1:10,labels=as.character(1:10))+
  theme(main="Final Teste by intial position chunk")+
  facet_grid(.~correct_appear_label)
  # theme_classic()


##############################3 Initial Order

df_finalFoil_toappend = df_pl_with_init%>% 
  mutate(correct=case_when(correct=="True"~1,
                           correct=="False"~0,
                           TRUE ~ correct))%>%
  filter(task=="finalTest",stimulusConditions=="FF")%>%
  mutate(type_comment="Final F" ) %>%
  mutate(correct_appear_label = " Final Foil")%>%
  mutate(init_outcome = 999)%>% #first or second time in initail correct =0 becuase didn't appear
  select(task, condition,type_comment, listNum_appear1_initial, subject_id,init_outcome,correct_appear_label, correct)

ditaf_in_order = df_pl_with_init%>% 
  mutate(correct=case_when(correct=="True"~1,
                           correct=="False"~0,
                           TRUE ~ correct))%>%
  filter(task=="finalTest")%>%
  mutate(correct_appear1=case_when(correct_appear1=="true"~1,
                                   correct_appear1=="false"~0,
                                   TRUE ~ 5 ) )%>%
    mutate(correct_appear2=case_when(correct_appear2=="true"~1,
                                   correct_appear2=="false"~0,
                                   TRUE ~ 5 ) )%>%
  mutate(type_comment = "Final T" )%>% #these are all final targets
  pivot_longer(cols=c(correct_appear1,correct_appear2),names_to="correct_appear_label",values_to="init_outcome")%>%
    mutate(listNum_appear1_initial=listNum_appear1_initial)%>%
  select(task, condition,type_comment, listNum_appear1_initial, subject_id,init_outcome,correct_appear_label,correct)%>%
  #bind rows from df_finalFoil_toappend
  bind_rows(df_finalFoil_toappend)%>%
  mutate(correct_appear_label=case_when(correct_appear_label=="correct_appear1"~"Target - by first appearance correction",
                                        correct_appear_label=="correct_appear2"~"Target - by second appearance correction",
                                        TRUE ~ correct_appear_label) )%>%
  filter(init_outcome!=5)%>% #take away the null for correct_appear both
  mutate(correct_appear1=init_outcome)%>%
  mutate(correct_appear1=case_when(correct_appear1==1~"Corrected Initial",
                                        correct_appear1==0 ~ "Wrong Initial",
                                   correct_appear1==999 ~"[Final FOIL initial not appear]",
                                        TRUE ~ "MISS") )%>%
         group_by(task, condition,type_comment, listNum_appear1_initial, subject_id,correct_appear1,correct_appear_label)%>%
         summarise(cr = mean(correct),se_cr = sd(correct,na.rm = TRUE) / sqrt(n()))%>%
         group_by(task, condition,type_comment, listNum_appear1_initial,correct_appear1,correct_appear_label)%>%
         summarise(cr = mean(cr), se_cr = mean(se_cr))%>%
  mutate(correct_appear1=as.factor(correct_appear1),correct_appear_label=as.factor(correct_appear_label))%>%
  mutate(listNum_appear1_initial=as.integer(listNum_appear1_initial))



ggplot(data=ditaf_in_order)+
  geom_line(aes(x=listNum_appear1_initial, y= cr ,group=interaction(task,type_comment,correct_appear1,correct_appear_label ),color= type_comment,linetype=correct_appear1),size=1)+ 
  
    geom_point(aes(x=listNum_appear1_initial, y= cr ,group=interaction(task,type_comment,correct_appear1,correct_appear_label  ),color= type_comment,shape=correct_appear1),size=4)+ 
  facet_grid(.~task)+ 
  # scale_color_manual(values=c("Target: studied and tested at (n), Foil (n+1)"="purple","Studied-only (n); Foil (n+1)"="green", 
  #            "Target: : started and tested at (n) ; Appear once" ="purple",
  #            "Foil(n), Foil (n+1)" ="blue",
  #            "Foil(n); Appear once" ="blue", 
  #            "Studied-only (n); Appear once" = "green",
  #            "Final Foil"="red" ),breaks=levelsStr_fn )+
  # scale_shape_discrete(breaks=levelsStr_fn)+
  # scale_linetype_discrete(breaks=levelsStr_fn)+
  #set x axis break to be descrete 1-10
  scale_x_continuous(breaks=1:10,labels=as.character(1:10))+
  theme(main="Final Teste by intial position chunk")+
  facet_grid(.~correct_appear_label)
  # theme_classic()

############################Combined plot

d1taf_combined= d1taf %>% 
  mutate(which_order="Final Test Order")%>%
  bind_rows(ditaf_in_order %>% mutate(which_order="Initial Test Order")) 
  
ggplot(data=d1taf_combined)+
  geom_line(aes(x=listNum_appear1_initial, y= cr ,group=interaction(task,type_comment,correct_appear1,correct_appear_label,which_order ),color= type_comment,linetype=correct_appear1),size=1)+ 
  
    geom_point(aes(x=listNum_appear1_initial, y= cr ,group=interaction(task,type_comment,correct_appear1,correct_appear_label,which_order  ),color= type_comment,shape=correct_appear1),size=4)+ 
  facet_grid(.~task)+ 
  scale_x_continuous(breaks=1:10,labels=as.character(1:10))+
  theme(main="Final Teste by intial position chunk")+
  # facet_grid(which_order~correct_appear_label)
  facet_wrap(which_order ~ correct_appear_label, ncol=3)
  # theme_classic()
```



type_comment_levels (that appears in initial test plots for test position: 
[1] "current target, in next trial"                 
[2] "current target, in next trial, from last trial"
[3] "current target, not in next trial"             
[4] "studied only, in next trial, from last trial"  
[5] "tested only, in next trial"                    
[6] "tested only, in next trial, from last trial"   
[7] "tested only, not in next trial"

into Segmented type comment
[1] "Foil-confusing, CR, double appear last list"
[2] "Foil-confusing, CR, single appear last list"
[3] "Foil-new, CR"                               
[4] "Target, Hits" 
index use above 
1,3
2,
4,6,
5,7



typecomment_in_levels
[1] "Inherented Foil - Last Foil"         "Inherented Foil - Last Studied Only"
[3] "Inherented Foil - Last Target"       "New Foil"                           
[5] "Target"   


## Segment list 2 plot (for test position)


```{r}
type_comment_levels= levels(as.factor(df_rt_pl$type_comment))[c(1,2,3,6,8,9,10)]
type_comment_levels
d1taqq123 = df_rt_pl%>% 
  filter(task=="initialTest_response")%>%
         group_by(task, condition,type_comment, studyPos_appear0_initial,subject_id )%>%
  # mutate(studyPos_appear0_initial=as.numeric(studyPos_appear0_initial))%>%
  mutate(studyPos_appear0_initial=as.numeric(testPos_appear0_initial))%>%
  mutate(studyPos_appear0_initial= if_else(studyPos_appear0_initial<=15, 'g1','g2') )%>%
  filter(listNum_appear1_initial==2)%>%
         summarise(cr = mean(correct))%>%
  # group Hits + two kinds CR
  mutate(group_section = case_when(type_comment%in%type_comment_levels[c(1,3)]~ "Target, Hits",
                                   type_comment%in%type_comment_levels[2] ~ "Foil-confusing, CR, double appear last list" ,
                                   type_comment%in%type_comment_levels[c(4,6)] ~ "Foil-confusing, CR, single appear last list",
                                   type_comment%in%type_comment_levels[c(5,7)] ~ "Foil-new, CR",
  ))%>%
  group_by(task, condition,group_section, studyPos_appear0_initial )%>%
         summarise(cr = mean(cr))
  
ggplot(data=d1taqq123)+
  geom_line(aes(x=studyPos_appear0_initial, y= cr ,group=interaction(task,group_section ),color= group_section,linetype=group_section))+ 
  geom_point(aes(x=studyPos_appear0_initial,y=cr,group=interaction(task,group_section),shape=group_section,color=group_section),size=4)+
  facet_grid(.~task)+
  scale_color_manual(values=c("green","green","blue","purple"))+
  xlab("Test position")



################################

d1taqq123 = df_rt_pl%>% 
  filter(task=="initialTest_response")%>%
         group_by(task, condition,type_comment, studyPos_appear0_initial,subject_id )%>%
  # mutate(studyPos_appear0_initial=as.numeric(studyPos_appear0_initial))%>%
  mutate(studyPos_appear0_initial=as.numeric(testPos_appear0_initial))%>%
  mutate(studyPos_appear0_initial= if_else(studyPos_appear0_initial<=15, 'g1','g2') )%>%
  filter(listNum_appear1_initial==2)%>%
         summarise(cr = mean(correct))%>%
  # group Hits + two kinds CR
  mutate(group_section = case_when(type_comment%in%type_comment_levels[c(1,3, 2)]~ "Target(Hits) + ConfuseF(CR)-double appear ",
                                   type_comment%in%type_comment_levels[c(1,3,4,6)] ~ "Target(Hits) + ConfuseF(CR)-single appear" ,
                                   type_comment%in%type_comment_levels[c(1,3, 5,7)] ~ "Target(Hits) + NewF(CR)",
  ))%>%
  group_by(task, condition,group_section, studyPos_appear0_initial )%>%
         summarise(cr = mean(cr))
  
ggplot(data=d1taqq123)+
  geom_line(aes(x=studyPos_appear0_initial, y= cr ,group=interaction(task,group_section ),color= group_section,linetype=group_section))+ 
  geom_point(aes(x=studyPos_appear0_initial,y=cr,group=interaction(task,group_section),shape=group_section,color=group_section),size=4)+
  facet_grid(.~task)+
  scale_color_manual(values=c("green","forestgreen","blue","purple"))+
  xlab("Test position")


```


### Segment list 1-10

>levels(as.factor(df_rt_pl$typecomment_in))
[1] "Inherented Foil - Last Foil"        
[2] "Inherented Foil - Last Studied Only"
[3] "Inherented Foil - Last Target"      
[4] "New Foil"                           
[5] "Target"                             

>into Segmented type comment
[1] "Foil-confusing, CR, double appear last list"
[2] "Foil-confusing, CR, single appear last list"
[3] "Foil-new, CR"                               
[4] "Target, Hits"

weighted sum:
 the mu overall here is actually applies to avg of targets (as all), or avg of foils (as all) 
$$
\mu_{\text{overall}}
= \frac{1}{N} \sum_{i=1}^K n_i \,\mu_i
= \frac{\sum_{i=1}^K n_i \,\mu_i}{\sum_{i=1}^K n_i}
\quad,\quad
N = \sum_{i=1}^K n_i.
$$

```{r}
typecomment_in_levels = levels(as.factor(df_rt_pl$typecomment_in))
typecomment_segment_levels = levels(as.factor(d1taqq123$group_section))

d1ta = df_rt_pl%>%
  filter(!is.na(rt),rt<3000)%>%
  filter(task=="initialTest_response")%>%
  # mutate(colorskeme=type_comment)%>%
  mutate(typecomment_in = case_when(
    typecomment_in %in% typecomment_in_levels[c(1,2)] ~ typecomment_segment_levels[2],
    typecomment_in %in% typecomment_in_levels[c(3)] ~ typecomment_segment_levels[1],
    typecomment_in %in% typecomment_in_levels[c(4)] ~ typecomment_segment_levels[3],
    typecomment_in %in% typecomment_in_levels[c(5)] ~ typecomment_segment_levels[4]
    )  )%>%
  mutate(colorskeme=typecomment_in)%>%
         group_by(task, condition, listNum_appear0_initial,colorskeme,subject_id)%>%
         summarise(cr = mean(correct))%>%
         group_by(task, condition, listNum_appear0_initial,colorskeme)%>%
         summarise(cr = mean(cr))%>%
  mutate(listNum_appear0_initial=as.factor(listNum_appear0_initial))
  # mutate(type_comment=as.factor(type_comment))
  
levelsStr = c("Foil-new, CR", "Target, Hits", "Foil-confusing, CR, double appear last list" ,
             "Foil-confusing, CR, single appear last list") 
ggplot(data=d1ta)+
  geom_line(aes(x=listNum_appear0_initial, y= cr ,group=interaction(task,colorskeme),color= colorskeme,linetype=colorskeme))+ 
  geom_point(aes(x=listNum_appear0_initial,y=cr,group=interaction(task,colorskeme),color=colorskeme,shape=colorskeme),size =4 )+
  facet_grid(.~task)+
  scale_color_manual(values=c("green","forestgreen","blue","purple"))


#########################################################3
# ok,... above is actually not what wanted
typecomment_in_levels = levels(as.factor(df_rt_pl$typecomment_in))
typecomment_segment_levels = levels(as.factor(d1taqq123$group_section))
simple_segment = c("Foil all - CR",
                   "Target all - CR")

d1ta = df_rt_pl%>%
  filter(!is.na(rt),rt<3000)%>%
  filter(task=="initialTest_response")%>%
  # filter(complete.cases(correct))%>%
  ungroup()%>%
  # mutate(colorskeme=type_comment)%>%
  mutate(colorskeme=typecomment_in)%>% #typecomment_in is a true diff item kinds group
  mutate(colorskeme = case_when( #colorskeme is a simple group
        colorskeme %in% typecomment_in_levels[1:4] ~ simple_segment[1],
        colorskeme == typecomment_in_levels[5] ~ simple_segment[2]
        )  )%>% #reapply groupby and summarize, groupby the new colorskeme
   group_by(task, condition, listNum_appear0_initial,typecomment_in,colorskeme,subject_id)%>%
      summarise(ni = n(),mui= mean(correct), ni_times_mui= ni*mui,sei= sd(correct)/sqrt(ni))%>% #get small group mean and n
  
  #below commentd: not add subid as group first, but calculated se_g, the next lines doesn't
  # part 1 comment
    group_by(task, condition, listNum_appear0_initial,colorskeme)%>% #CATION: should add subject_id here as first avg???
  summarise(n_g=n(), weight_avg = sum(ni_times_mui)/n_g,se_g=sqrt(sum(ni^2 * sei^2)/n_g), mumui=mean(mui))%>%
  mutate(weight_avg=mumui)%>%
  
  #part 2 comment
  # group_by(task, condition, listNum_appear0_initial,colorskeme, subject_id)%>% #CATION: should add subject_id here as first avg???
  #   summarise(n_g=n(), weight_avg = sum(ni_times_mui)/n_g)%>%
  # group_by(task, condition, listNum_appear0_initial,colorskeme)%>%
  #   summarise(weight_avg=mean(weight_avg), se_g = sd(weight_avg)/sqrt(n()))%>% #this seg might be in correct

   group_by(task, condition, listNum_appear0_initial)%>%
         mutate(all_avg = mean(weight_avg))
  # mutate(type_comment=as.factor(type_comment))
  
# # [1] "Foil-confusing, CR, double appear last list"
# # [2] "Foil-confusing, CR, single appear last list"
# # [3] "Foil-new, CR"                               
# # [4] "Target, Hits" 

# for alpha able to appear
# library(grDevices)
# options(bitmapType='cairo')

ggplot(data=d1ta)+
  geom_line(aes(x=listNum_appear0_initial, y= weight_avg ,group=interaction(task,colorskeme),color= colorskeme,linetype=colorskeme))+ 
  geom_point(aes(x=listNum_appear0_initial,y=weight_avg,group=interaction(task,colorskeme),color=colorskeme,shape=colorskeme),size =4 )+
  # geom_ribbon(aes(x=listNum_appear0_initial, ymin=weight_avg-se_g, ymax=weight_avg+se_g, fill=colorskeme),alpha=0.2)+
  # geom_errorbar(aes(x=listNum_appear0_initial, ymin=weight_avg-se_g, ymax=weight_avg+se_g), width=.1, position=position_dodge(0.05)) +
  geom_line(aes(x=listNum_appear0_initial,y=all_avg),color="black")+
  facet_grid(.~task)
  # scale_color_manual(values=c("green","forestgreen","blue","purple"))



```

### Segment Avg plot way 2
```{r}

type_comment_levels= levels(as.factor(df_rt_pl$type_comment))[c(1,2,3,6,8,9,10)]
type_comment_levels
                   
d1ta = df_rt_pl%>%
  filter(!is.na(rt),rt<3000)%>%
  filter(task=="initialTest_response")%>%
  # filter(complete.cases(correct))%>%
  ungroup()%>%
  # mutate(colorskeme=type_comment)%>%
  mutate(colorskeme = case_when(type_comment%in%type_comment_levels[c(1,3, 2)]~ "Target(Hits) + ConfuseF(CR)-double appear ",
                                   type_comment%in%type_comment_levels[c(1,3,4,6)] ~ "Target(Hits) + ConfuseF(CR)-single appear" ,
                                   type_comment%in%type_comment_levels[c(1,3, 5,7)] ~ "Target(Hits) + NewF(CR)",
  ))%>%
  # mutate(colorskeme=typecomment_in)%>% #typecomment_in is a true diff item kinds group
  # mutate(colorskeme = case_when( #colorskeme is a simple group
  #       colorskeme %in% typecomment_in_levels[1:4] ~ simple_segment[1],
  #       colorskeme == typecomment_in_levels[5] ~ simple_segment[2]
  #       )  )%>% #reapply groupby and summarize, groupby the new colorskeme
   group_by(task, condition, listNum_appear0_initial,type_comment,colorskeme,subject_id)%>%
      summarise(ni = n(),mui= mean(correct), ni_times_mui= ni*mui,sei= sd(correct)/sqrt(ni))%>% #get small group mean and n
  
  
  #below commentd: not add subid as group first, but calculated se_g, the next lines doesn't
  # part 1 comment
    group_by(task, condition, listNum_appear0_initial,colorskeme)%>% #CATION: should add subject_id here as first avg???
  summarise(n_g=n(), weight_avg = sum(ni_times_mui)/n_g,se_g=sqrt(sum(ni^2 * sei^2)/n_g), mumui=mean(mui))%>%
  mutate(weight_avg=mumui)%>%
  
   group_by(task, condition, listNum_appear0_initial)%>%
         mutate(all_avg = mean(weight_avg))
  # mutate(type_comment=as.factor(type_comment))
  

# library(grDevices)
# options(bitmapType='cairo')

ggplot(data=d1ta)+
  geom_line(aes(x=listNum_appear0_initial, y= weight_avg ,group=interaction(task,colorskeme),color= colorskeme,linetype=colorskeme))+ 
  geom_point(aes(x=listNum_appear0_initial,y=weight_avg,group=interaction(task,colorskeme),color=colorskeme,shape=colorskeme),size =4 )+
  # geom_ribbon(aes(x=listNum_appear0_initial, ymin=weight_avg-se_g, ymax=weight_avg+se_g, fill=colorskeme),alpha=0.2)+
  # geom_errorbar(aes(x=listNum_appear0_initial, ymin=weight_avg-se_g, ymax=weight_avg+se_g), width=.1, position=position_dodge(0.05)) +
  geom_line(aes(x=listNum_appear0_initial,y=all_avg),color="black")+
  facet_grid(.~task)
  # scale_color_manual(values=c("green","forestgreen","blue","purple"))


```




### debug
```{r}
d1ta = df_rt_pl%>%
  filter(!is.na(rt),rt<3000)%>%
  filter(task=="initialTest_response")%>%
  # filter(complete.cases(correct))%>%
  ungroup()%>%
  # mutate(colorskeme=type_comment)%>%
  mutate(colorskeme=typecomment_in)%>% #typecomment_in is a true diff item kinds group
  mutate(colorskeme = case_when( #colorskeme is a simple group
        colorskeme %in% typecomment_in_levels[1:4] ~ simple_segment[1],
        colorskeme == typecomment_in_levels[5] ~ simple_segment[2]
        )  )%>% #reapply groupby and summarize, groupby the new colorskeme
   group_by(task, condition, listNum_appear0_initial,typecomment_in,colorskeme,subject_id)%>%
  summarise(meanscore = mean(correct))%>%
   group_by(task, condition, listNum_appear0_initial,typecomment_in,colorskeme)%>%
      summarise(ni = n(),mui= mean(meanscore), ni_times_mui= ni*mui,sei= sd(meanscore)/sqrt(ni))%>% #get small group mean and n
  
  #below commentd: not add subid as group first, but calculated se_g, the next lines doesn't
  # part 1 comment
    group_by(task, condition, listNum_appear0_initial,colorskeme)%>% #CATION: should add subject_id here as first avg???
  summarise(n_g=n(), weight_avg = sum(ni_times_mui)/n_g, se_g=sqrt(sum(ni^2 * sei^2)/n_g), mumui=mean(mui))%>%
  # mutate(weight_avg=mumui)%>%
  
  #part 2 comment
  # group_by(task, condition, listNum_appear0_initial,colorskeme, subject_id)%>% #CATION: should add subject_id here as first avg???
  #   summarise(n_g=n(), weight_avg = sum(ni_times_mui)/n_g)%>%
  # group_by(task, condition, listNum_appear0_initial,colorskeme)%>%
  #   summarise(weight_avg=mean(weight_avg), se_g = sd(weight_avg)/sqrt(n()))%>% #this seg might be in correct

   group_by(task, condition, listNum_appear0_initial)%>%
         mutate(all_avg = mean(weight_avg))
  # mutate(type_comment=as.factor(type_comment))
  
# # [1] "Foil-confusing, CR, double appear last list"
# # [2] "Foil-confusing, CR, single appear last list"
# # [3] "Foil-new, CR"                               
# # [4] "Target, Hits" 

# for alpha able to appear
# library(grDevices)
# options(bitmapType='cairo')

ggplot(data=d1ta)+
  geom_line(aes(x=listNum_appear0_initial, y= weight_avg ,group=interaction(task,colorskeme),color= colorskeme,linetype=colorskeme))+ 
  geom_point(aes(x=listNum_appear0_initial,y=weight_avg,group=interaction(task,colorskeme),color=colorskeme,shape=colorskeme),size =4 )+
  # geom_ribbon(aes(x=listNum_appear0_initial, ymin=weight_avg-se_g, ymax=weight_avg+se_g, fill=colorskeme),alpha=0.2)+
  # geom_errorbar(aes(x=listNum_appear0_initial, ymin=weight_avg-se_g, ymax=weight_avg+se_g), width=.1, position=position_dodge(0.05)) +
  geom_line(aes(x=listNum_appear0_initial,y=all_avg),color="black")+
  facet_grid(.~task)
```



# Indv difference
```{r}
library(tidyverse)
names(df_rt_pl)
d1t_indv = df_rt_pl%>% 
  filter(task=="initialTest_response")%>%
      mutate(listNum_appear0_initial=as.numeric(listNum_appear0_initial))%>%
      # arrange(ip, listNum_appear0_initial,)%>%
      filter(listNum_appear0_initial<=4)%>%
      mutate(colorskeme = case_when(current_assignmentTypesWithinList =="T_target" & is_currentObjAppear1=="true" ~"Target studied from current list",
                                is_currentObjAppear1=="false"  ~ paste("Foil from last trial",type_comment),
                                  current_assignmentTypesWithinList =="T_foil"  ~"Foil current list"))%>%
          group_by(task, condition, listNum_appear0_initial,colorskeme,subject_id)%>%
          #task and condition is useless here because they only have one level
         summarise(cr = mean(correct), se = sd(correct) / sqrt(n()))%>%
         filter(colorskeme=="Target studied from current list",listNum_appear0_initial %in% c(2,3) )%>%
        mutate(subject_id = reorder(subject_id, cr))



p_indvdiff = ggplot(data=d1t_indv, aes(x=subject_id, group=interaction(condition,task,colorskeme, listNum_appear0_initial),color=colorskeme))+
  geom_line(aes(y=cr))+
  geom_point(aes(y=cr,shape=colorskeme),size =4 )+
  geom_errorbar(aes(ymin=cr-se, ymax=cr+se), width=.1, position=position_dodge(0.05)) +
  facet_grid(listNum_appear0_initial~.)+
  scale_color_manual(values=c("blue","green","green","green","purple"))+
  theme(legend.position = "none")
p_indvdiff


d1t_indv = df_rt_pl%>% 
  filter(task=="initialTest_response")%>%
      mutate(listNum_appear0_initial=as.numeric(listNum_appear0_initial))%>%
      # arrange(ip, listNum_appear0_initial,)%>%
      filter(listNum_appear0_initial%in%c(2,3))%>%
      # mutate(colorskeme = case_when(current_assignmentTypesWithinList =="T_target" & is_currentObjAppear1=="true" ~"Target studied from current list",
      #                           is_currentObjAppear1=="false"  ~ paste("Foil from last trial",type_comment),
      #                             current_assignmentTypesWithinList =="T_foil"  ~"Foil current list"))%>%
      mutate(colorskeme = case_when(
                type_comment %in% c("current target, in next trial","current target, not in next trial" ) ~"Target studied from current list",
                type_comment %in% c("tested only, in next trial","tested only, not in next trial" )  ~ "Foil current trial",
                TRUE~ paste("foil-lastTrial",type_comment)))%>%
          # group_by(task, condition, listNum_appear0_initial,colorskeme,subject_id)%>%
          # task and condition is useless here because they only have one level
         # summarise(cr = mean(correct), se = sd(correct) / sqrt(n()))%>%
         select(task,condition,colorskeme,subject_id,correct,listNum_appear0_initial)%>%
         group_by(task, condition, colorskeme,subject_id,listNum_appear0_initial)%>%
         summarise(correct = mean(correct))%>% #because each categories of that subject has more than 1 trial, so calculate performace of particiaptn i on specific condition first (.e.g average 3 trials performance in this condition)
        pivot_wider(names_from = listNum_appear0_initial, values_from = c(correct))%>% 
        ungroup()%>%
        # %>%
        mutate(cr_diff = `3` - `2`) %>%
        #%>%   
filter(!is.na(rt))%>%
# filter(!is.na(rt),rt<3000)%>%
        mutate(colorskeme=as.factor(colorskeme), subject_id=as.factor(subject_id))%>%
          group_by(task, condition,colorskeme,subject_id)%>%
          summarise(mean_cr_diff = mean(cr_diff), se_cr_diff = sd(cr_diff) / sqrt(n()))%>%
          # %>%
        #  filter(listNum_appear0_initial %in% c(2,3) )%>%
        mutate(colorskeme = factor(colorskeme, levels = c(levels(colorskeme)[5], levels(colorskeme)[-5])))%>%
        mutate(subject_id = reorder(subject_id, mean_cr_diff))

# d1t_indv$cr_diff
d1_density=d1t_indv %>% 
group_by(colorskeme) %>%
  summarise(density_data = list(density(mean_cr_diff, na.rm = TRUE))) %>%
  mutate(density_x = map(density_data, ~ .x$x),
    density_y = map(density_data, ~ .x$y)) %>%
  select(-density_data) %>%
  unnest(c(density_x, density_y))

d1_density

density_y = d1_density %>%
  group_by(colorskeme) %>%
  filter(density_y == max(density_y)) 

ggplot(data=d1t_indv)+
  geom_density(aes(x=mean_cr_diff, fill=colorskeme,color=colorskeme,), alpha=0.5) +
  # stat_density(aes(x=mean_cr_diff, fill=colorskeme), geom="line", position="identity") +
  geom_vline(data = density_y, aes(xintercept = density_x, color = colorskeme), linetype="dashed") +
  geom_text(data = density_y, 
        aes(x = density_x, label = round(density_x, 2), y = 0.5), angle = 90, vjust = -0.5, hjust = 1.2, size=5)+
  # facet_wrap(~colorskeme, scales = "free") +
  facet_wrap(~colorskeme) +
  theme_minimal() +
  theme(text = element_text(size = 12), legend.position = "null")+
  scale_fill_manual(values=c("purple","blue","green","green","green"))

# p_indvdiff = ggplot(data=d1t_indv, aes(x=subject_id,y=cr,
#                             group=interaction(condition,task,colorskeme),color=colorskeme))+
#   geom_line(aes(y=cr))+
#   geom_point(aes(y=cr,shape=colorskeme),size =4 )+
#   geom_errorbar(aes(ymin=cr-se, ymax=cr+se), width=.1, position=position_dodge(0.05)) +
#   facet_grid(colorskeme~.)+
#   scale_color_manual(values=c("blue","green","green","green","purple"))+
#   theme(text = element_text(size = 30))+
#   geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   scale_x_discrete(labels = function(x) substr(x, 1, 3))
#   # theme(legend.position = "none")
#   # ylim(c(-1.5,1.5))
# p_indvdiff


  # theme(legend.position = "none")
```

## Distribution plot for only 1 condition
```{r}
d1t_indv = df_rt_pl%>% 
  filter(task=="initialTest_response")%>%
      mutate(listNum_appear0_initial=as.numeric(listNum_appear0_initial))%>%
      mutate(colorskeme = case_when(
                type_comment %in% c("current target, in next trial","current target, not in next trial" ) ~"Target studied from current list",
                type_comment %in% c("tested only, in next trial","tested only, not in next trial" )  ~ "Foil current trial",
                TRUE~ paste("foil-lastTrial",type_comment)))%>%

         select(task,condition,colorskeme,subject_id,correct,listNum_appear0_initial)%>%
         filter(listNum_appear0_initial %in% c(2,3) )%>%
         group_by(task, condition, colorskeme,subject_id,listNum_appear0_initial)%>%
         summarise(mean_cr_diff = mean(correct))%>%
        ungroup()%>%
  mutate(colorskeme=as.factor(colorskeme))%>%
        mutate(colorskeme = factor(colorskeme, levels = c(levels(colorskeme)[5], levels(colorskeme)[-5])))%>%
        mutate(subject_id = reorder(subject_id, mean_cr_diff))
d1t_indv
# d1t_indv$cr_diff
# d1_density=d1t_indv %>% 
# group_by(colorskeme) %>%
#   summarise(density_data = list(density(mean_cr_diff, na.rm = TRUE))) %>%
#   mutate(density_x = map(density_data, ~ .x$x),
#     density_y = map(density_data, ~ .x$y)) %>%
#   select(-density_data) %>%
#   unnest(c(density_x, density_y))

# d1_density
# 
# density_y = d1_density %>%
#   group_by(colorskeme) %>%
#   filter(density_y == max(density_y)) 

ggplot(data=d1t_indv)+
  geom_density(aes(x=mean_cr_diff, fill=colorskeme,color=colorskeme, group=interaction(colorskeme,listNum_appear0_initial)), alpha=0.5) +
  # stat_density(aes(x=mean_cr_diff, fill=colorskeme), geom="line", position="identity") +
  # facet_wrap(~listNum_appear0_initial) +
  theme_minimal() +
    facet_grid(listNum_appear0_initial~colorskeme) +
  theme(text = element_text(size = 10))+
  scale_fill_manual(values=c("purple","blue","green","green","green"))

```



#inferential statistics
```{r}
#performance in category
d_perform = df_rt_pl%>% 
  filter(task=="initialTest_response")%>%
      mutate(listNum_appear0_initial=as.numeric(listNum_appear0_initial))%>%
      filter(listNum_appear0_initial%in%c(2,3))%>%
      mutate(colorskeme = case_when(
                type_comment %in% c("current target, in next trial","current target, not in next trial" ) ~"Target studied from current list",
                type_comment %in% c("tested only, in next trial","tested only, not in next trial" )  ~ "Foil current trial",
                TRUE~ paste("foil-lastTrial",type_comment)))%>%
                filter(!is.na(rt))%>%
         select(colorskeme,subject_id,correct,listNum_appear0_initial)%>%
         group_by(colorskeme,subject_id,listNum_appear0_initial)%>%
         summarise(correct = mean(correct))



d_perform

# Perform paired t-test for each colorskeme category
# library(dplyr)
# library(tidyr)

# Reshape data for paired t-test
d_perform_wide <- d_perform %>%
  pivot_wider(names_from = listNum_appear0_initial, values_from = correct, names_prefix = "list_") %>%
  filter(!is.na(list_2) & !is.na(list_3)) # Ensure no missing values for paired t-test

# Perform paired t-test for each colorskeme
t_test_results <- d_perform_wide %>%
  group_by(colorskeme) %>%
  summarise(
    t_test = list(t.test(list_2, list_3, paired = TRUE, alternative = "two.sided")),
    .groups = "drop"
  ) %>%
  mutate(
    p_value = map_dbl(t_test, ~ .x$p.value),
    t_statistic = map_dbl(t_test, ~ .x$statistic)
  )

# Display results
t_test_results %>%
  select(colorskeme, t_statistic, p_value)

 
```


Foil current trial                                   0.983  
foil-lastTrial current target, in next trial, from … 0.00731
foil-lastTrial studied only, in next trial, from la… 0.968  
foil-lastTrial tested only, in next trial, from las… 0.834 
Target studied from current list                     0.00814

## bayesian way
```{r}
 # Perform Bayesian paired t-test for each colorskeme category
#   library(BayesFactor)
# 
#   # Reshape data for Bayesian paired t-test
#   d_perform_wide <- d_perform %>%
#     pivot_wider(names_from = listNum_appear0_initial, values_from = correct, names_prefix = "list_") %>%
#     filter(!is.na(list_2) & !is.na(list_3)) # Ensure no missing values
# 
#   # Perform Bayesian paired t-test for each colorskeme
#   bayesian_results <- d_perform_wide %>%
#     group_by(colorskeme) %>%
#     summarise(
#       bf = list(ttestBF(x = list_2, y = list_3, paired = TRUE)),
#       .groups = "drop"
#     ) %>%
#     mutate(
#       bf_value = map_dbl(bf, ~ exp(.x@bayesFactor$bf))
#     )
# 
# # BF > 1: Evidence favors the alternative hypothesis.
# # BF < 1: Evidence favors the null hypothesis.
# # BF ≈ 1: Evidence is inconclusive.
#   # Display results
#   bayesian_results %>%
#     select(colorskeme, bf_value)
```
