
```{r}
library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(stringr)
```


```{r}
# getwd()
# names=list.files("full_splitted_data_group1")
df = list.files(path = "./", pattern = "*.csv") %>% 
  map_df(~read_csv(.))
file_names <- list.files(path = "./", pattern = "*.csv", full.names = TRUE)
names(df)
```


```{r}
df$response[1]%>%class
df1 = df%>%
  filter(task%in%c("FR_task","cued_third"))%>%
  # summarize(n=n())
  group_by(response,run_id,task,free_recall,recall_correctness)%>%
  mutate(n=n())%>%
  distinct(response,run_id,task,n)%>%
  ungroup()
df1 

dfnew = df1
for (i in 2:10){
  deletedrows = df1[df1$n==i,] %>% mutate(free_recall=FALSE)
  deletedrows
  dfnew = dfnew %>%
    add_row(deletedrows)%>%
    arrange(run_id,task)
}

  # unique()
  # filter(n()>1)%>%
  # mutate(n_removed = case_when((n()>1) & (response!="NA") & response!='{"Q0":""}' &  ~ "duplicated",
                               # TRUE ~ "ok"))
  # filter(duplicated(.[["response"]]))
which(df$response=="{\"Q0\":\"kitchen\"}")
```


```{r}
df1 = df%>%
  filter(task%in%c("FR_task","cued_third"))%>%
  group_by(response,run_id,task,free_recall,recall_correctness)%>%
  mutate(n_removed = case_when((n()>1) & (response!="NA") & response!='{"Q0":""}'  ~ "duplicated",
                               TRUE ~ "ok"))
df1[df1$n_removed=="duplicated",]


df %>% 
  filter(task%in%c("FR_task","cued_third"))%>%
  group_by(response,run_id,task,free_recall,recall_correctness)%>%
  add_tally()
                               
```

```{r}


```


```{r}
safe_json_parse <- function(response) {
  tryCatch({
    # print( fromJSON(response)$Q0)
    word <- fromJSON(response)$Q0
    if(word != "") {
      return(word)
    } else {
      return(NA_character_)
    }
  }, error = function(e) {
    return(NA_character_)
  })
}
df$free_recall_word <- sapply(df$response, safe_json_parse)

# df_A2E <- df %>%
#   group_by(run_id) %>%
#   mutate(
#     right_FR_words = list(unique(unlist(strsplit(as.character(free_recall_word[task == "FR_task" & free_recall == TRUE]), ", ")))))
    # cued_third_words = list(unique(as.character(correct_response[task == "cued_third"]))),
    # non_cued_FR_words = list(setdiff(right_FR_words[[1]], cued_third_words[[1]])))
# df_A2E$cued_third_words

```

    A = ifelse(task == "FR_task" & free_recall == TRUE & extracted_word %in% non_cued_FR_words[[1]], 
               sapply(extracted_word, process_word, processed_words_A), 0),
    
    B = ifelse(task == "cued_third" & cued_third_recall_correctness == 1 & extracted_word %in% right_FR_words[[1]], 1, 0),
    
    C = ifelse(task == "cued_third" & cued_third_recall_correctness == 0 & extracted_word %in% right_FR_words[[1]],
               sapply(extracted_word, process_word, processed_words_C), 0),
    D = A + B + C,
    
    E = ifelse(task == "cued_third" & recall_correctness == 1 & !extracted_word %in% right_FR_words[[1]],
               sapply(extracted_word, process_word, processed_words_E)[[1]], 0)
```{r}
# df%>%filter(run_id==3,response=="{\"Q0\":\"river\"}")
# df$response
# df$response[1]%>%class
df1 = df%>%
  filter(task%in%c("FR_task","cued_third"))%>%
  group_by(response,run_id,task,free_recall,recall_correctness)%>%
  # mutate(n_removed = case_when((n()>1) & (response!="NA") & response!='{"Q0":""}'  ~ "duplicated",
  # TRUE ~ "ok"))%>%
  mutate(count_duplicated = row_number()) %>%
  mutate(count_duplicated = case_when(response%in%c("NA",'{"Q0":""}',NA)  ~ 1,
                                      TRUE ~ count_duplicated))%>%
  mutate(FR_correct= case_when(count_duplicated>1&task=="FR_task"~0,
                               TRUE ~ free_recall))%>%
  mutate(CR_correct= case_when(count_duplicated>1&task=="cued_third"~0,
                               TRUE ~ recall_correctness))%>%
  

df1

```












