
```{r}
library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(stringr)
```


```{r}
# getwd()
# names=list.files("full_splitted_data_group1")
df = list.files(path = "./", pattern = "*.csv") %>% 
  map_df(~read_csv(.))%>%
  filter(task%in%c("FR_task","cued_third"))%>%
  group_by(response,run_id,task,free_recall,recall_correctness)%>%
  mutate(count_duplicated = row_number()) %>%
  mutate(count_duplicated = case_when(response%in%c("NA",'{"Q0":""}',NA)  ~ 1,
                                      TRUE ~ count_duplicated))%>%
  mutate(FR_correct= case_when(count_duplicated>1&task=="FR_task"~0,
                               TRUE ~ free_recall))%>%
  mutate(CR_correct= case_when(count_duplicated>1&task=="cued_third"~0,
                               TRUE ~ recall_correctness))%>%
  mutate(response = strsplit(response, split='"')[[1]][4])
file_names <- list.files(path = "./", pattern = "*.csv", full.names = TRUE)
names(df)
df
```



```{r}
 strsplit('moment;opinion;level;place;reason', split=';')
```

  
```{r}
'%stringin%'=function(x,y) grepl(x, y, fixed=TRUE);
# "engine"%stringin%'{"Q0":"engine"}'


df_cued_third_words = df%>%filter(task=="cued_third")%>%
  group_by(run_id,correct_response)%>%
  aggregate(correct_response~run_id,FUN = paste,collapse = ";")%>%
  mutate(cued_third_words = strsplit(correct_response, split=';'))%>%
  select(run_id,cued_third_words)
df_cued_third_words #correct_response.y



df_right_FR_words = df%>%
  filter(task=="FR_task"&FR_correct==1) %>%
  group_by(run_id,response)%>%
  aggregate(response~run_id,FUN = paste,collapse = ";")%>%
  mutate(right_FR_words = strsplit(response, split=';'))%>%
  select(run_id,right_FR_words)
df_right_FR_words #response.y


df_wrong_CR_words = df%>%
  filter(task=="cued_third"&CR_correct==0) %>%
  group_by(run_id,correct_response)%>%
  aggregate(correct_response~run_id,FUN = paste,collapse = ";")%>%
  mutate(wrong_CR_words = strsplit(correct_response, split=';'))%>%
  select(run_id,wrong_CR_words)
df_wrong_CR_words #response.y


df_non_cued_FR_words =
  df %>% 
  filter(task=="FR_task"&FR_correct==1) %>%
  group_by(run_id,response)%>%
  summarize(n=n())%>%
  left_join(df_cued_third_words,by="run_id") %>%
  mutate(non_cued=case_when(response%in%cued_third_words[[1]] ~ 0,
                              TRUE ~ 1))%>%
  filter(non_cued==1)%>%
  aggregate(response~run_id,FUN = paste,collapse = ";") %>%
  mutate(non_cued_FR_words = strsplit(response, split=';'))%>%
  select(run_id,non_cued_FR_words) #response
df_non_cued_FR_words
#response.x correct_response.x is that original in df
  
  


# df_non_cued_FR_words = df %>% filter((task=="FR_task"&FR_correct==1) & ) %>%
#   group_by(run_id,response)%>%
#   aggregate(response~run_id,FUN = paste,collapse = ";")

dfnew = df %>%left_join(df_right_FR_words,by=c("run_id"))%>%
  left_join(df_cued_third_words,by=c("run_id"))%>%
  left_join(df_non_cued_FR_words,by=c("run_id"))%>%
  left_join(df_wrong_CR_words,by=c("run_id"))
  
  
  # mutate(non_cued_FR_words=response.x%stringin%response.y & !response.x%stringin%correct_response.y)
dfnew


```
  
  
  
  
  
  
  
    A = ifelse(task == "FR_task" & free_recall == TRUE & extracted_word %in% non_cued_FR_words[[1]], 
               sapply(extracted_word, process_word, processed_words_A), 0),
    
    B = ifelse(task == "cued_third" & cued_third_recall_correctness == 1 & extracted_word %in% right_FR_words[[1]], 1, 0),
    
    C = ifelse(task == "cued_third" & cued_third_recall_correctness == 0 & extracted_word %in% right_FR_words[[1]],
               sapply(extracted_word, process_word, processed_words_C), 0),
    D = A + B + C,
    
    E = ifelse(task == "cued_third" & recall_correctness == 1 & !extracted_word %in% right_FR_words[[1]],
               sapply(extracted_word, process_word, processed_words_E)[[1]], 0)
               
               
```{r}

safe_json_parse <- function(response) {
  tryCatch({
    word <- fromJSON(response)$Q0
    if(word != "") {
      return(word)
    } else {
      return(NA_character_)
    }
  }, error = function(e) {
    return(NA_character_)
  })
}
df$free_recall_word <- sapply(df$response, safe_json_parse)
df1 <- dfnew %>%
  group_by(run_id) %>%
  mutate(
    # right_FR_words = right_FR_words,
    # cued_third_words = correct_response.y,
    # non_cued_FR_words = response,
    cued_third_recall_correctness = recall_correctness,
    # Extract word from free_recall_word format
    extracted_word = response
    )
df1$non_cued_FR_words

# df2 = 
  df1%>%
  filter(task%in%c("FR_task","cued_third"))%>%
  mutate(A = case_when(task == "FR_task" & FR_correct == 1 & extracted_word %in% non_cued_FR_words[[1]]~"A",
                       task == "cued_third" & CR_correct == 1 & extracted_word %in% 
                         right_FR_words[[1]] ~ "B",
                        task == "FR_task" & extracted_word %in% right_FR_words[[1]] & 
                         extracted_word%in% wrong_CR_words[[1]] ~ "C"
                       ))%>%select(
  response,run_id,task,CR_correct,FR_correct,A
)
  
  # task == "cued_third" & CR_correct == 0 &

```



